---
title: "20181211_workflow_peakAnno"
author: "R_Krautz"
date: "11/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## [0.0.] Load necessary packages
```{r message=FALSE}
base::library(tidyverse)
base::library(magrittr)
base::library(here)
base::library(bedr)
```

##---------------------##
##----Prerequisites----##
##---------------------##

## [1.0.] annotater() function
```{r}
annotater <- function(
  df,
  chosenEngine = "bedtools",
  tssRef = anno,
  cols = base::c(
      chr = "V1",
      start = "V2",
      end = "V3",
      name ="V4",
      tssChr ="V5",
      tssStart = "V6",
      tssEnd = "V7",
      tssID = "V8",
      nd = "V9",
      tssStrand = "V10",
      ensembl_gene_id = "V11",
      external_gene_name = "V12",
      gene_biotype = "V13",
      entrezgene = "V14"
    )
  ){
    
    out <- tryCatch(
        {
          if(!bedr::check.binary(chosenEngine)){
            stop(
              base::paste0(
                  "Chosen engine:\t",chosenEngine,"\tnot available.\n"
                )
            )
          }else{
            
            is.df.valid <- df %>%
              base::as.data.frame() %>%
              bedr::is.valid.region(
                  check.chr = FALSE
                )
            
            dfVal <- df %>%
              dplyr::filter(
                  dplyr::row_number() == base::which(is.df.valid)
                ) %>% 
              base::as.data.frame()
            
            dfSort <- bedr::bedr(
                engine = chosenEngine,
                input = base::list(i=dfVal),
                method = "sort",
                params = "",
                check.chr = FALSE,
                check.valid = TRUE,
                check.sort = FALSE
              )
            
            dfAnno <- bedr::bedr(
                engine = chosenEngine,
                input = base::list(a = dfSort),
                method = "closest",
                params = base::paste("-b", tssRef, sep = " "),
                check.chr = FALSE,
                check.valid = TRUE,
                check.sort = FALSE
              )
            
            dfAnno %>%
              tibble::as_tibble() %>%
              dplyr::rename(.,!!!cols) %>% 
              dplyr::arrange(chr, start)
          }
        },
      error = function(cond){
          base::message(cond)
          return(NA)
        },
      warning = function(cond){
          base::message(cond)
          return(NA)
        }
      )
    return(out) 
  }
```

## [1.1.] Helper functions for injecting additional y-axis
```{r}
sequencer <- function(clus,start,end,gap=3L){
    return(
      base::seq(
        start + gap*(clus-1),
        end + gap*(clus-1)
      )
    )
  }
```

```{r}
seqAdd <- function(df, gap=30L){
  return(
    df %>%
      dplyr::mutate(
          clus = base::as.integer(clus),
          end = base::cumsum(amount),
          start = end-amount+1,
          seq = purrr::pmap(
            .l = base::list(
                clus,start,end
              ),
            .f = .GlobalEnv$sequencer,
            gap = gap
          )
        ) %>%
      tidyr::unnest(cols = "seq") %>%
      dplyr::select(seq) %>%
      base::unlist() %>%
      base::unname()
    )
}
```

## [1.2.] Annotation reference
#### Based on TSS definitions in 'create_annotations.Rmd'
```{r}
fn <- base::paste0(
     here::here("data/"),
    "BDGP6.bm.TssBiomart.ProteinCoding.bed"
  )

if(file.exists(fn)){
      anno <- fn
  }
```

## [1.3.] Load resKclus & resK
#### see [6.9.]-[6.10.] & [5.16.]-[5.17.] in 'cluster_peaks.Rmd'
```{r eval=FALSE,message=FALSE}
resKclus <- base::readRDS(
    file = base::list.files(
        path = here::here("data/"),
        full.names = TRUE
      ) %>%
    stringr::str_subset("resKclus")
  )

resK <- base::readRDS(
  file = base::list.files(
        path = here::here("data/"),
        full.names = TRUE
      ) %>%
    stringr::str_subset("resK")
  )
```

## [1.4.] Load FlyTFs
#### see 'https://www.mrc-lmb.cam.ac.uk/genomes/FlyTF/old_index.html'
#### dplyr::filter(tfs,symbol %in% base::c("grh","D","ey"))
```{r}
tfs <- readr::read_delim(
      file = base::paste0(
          here::here("resources/"),
          "FlyTFv1.all_candidates.csv"
        ),
      delim = "\t",
      col_names = TRUE,
      col_types = "cccccc",
      quote = ""
    ) %>%
  dplyr::filter(
      !base::is.na(verdict_TF)
    )
```

## [1.5.] Prerequisites
```{r}
groups <- tibble::tibble(
  profile = base::c(
      "DichaeteGal4_DichaeteGFP",
      "DichaeteGal4_GrainyheadGFP",
      "DichaeteGal4_EyelessGFP",
      "OgreGal4_DichaeteGFP",
      "OgreGal4_EyelessGFP"
    )
  )
repl <- tibble::tibble(
  sym = base::c("D","Grh","Ey"),
  profile = base::c(
      "DichaeteGal4_DichaeteGFP",
      "DichaeteGal4_GrainyheadGFP",
      "DichaeteGal4_EyelessGFP"
    )
  )
sel_chrom <- base::c(
    "2L", "2R", "3L", "3R", "4","MT", "X", "Y"
  )
```

##----------------------##
##----Data_wrangling----##
##----------------------##

## [2.0.] Inject additional y-axis
```{r}
preAnno__ <- resKclus %>%
  dplyr::mutate(
      kclus = base::factor(
        x = kclus,
        levels = base::seq(1,base::nrow(resK$centers)),
        ordered = TRUE
      )
    ) %>%
  dplyr::arrange(kclus,sil_width)

clusDis <- resKclus %>%
  dplyr::group_by(kclus) %>%
  dplyr::summarise(amount = dplyr::n()) %>% 
  dplyr::rename(., clus = kclus)

preAnno_ <- dplyr::mutate(
    .data = preAnno__,
    yInj = .GlobalEnv$seqAdd(clusDis, gap = 100L),
    cred = stringr::str_c(kclus,yInj,sep = "_")
  )
```

## [2.1.] Evaluate injected y-axis
```{r}
resKclus %>%
  dplyr::distinct(chr,start,end) %>%
  base::nrow()

preAnno_ %>%
  dplyr::group_by(kclus) %>%
  dplyr::filter(
      dplyr::row_number() %in% base::c(1,dplyr::n())
    )
```

## [2.2.] Prepare annotation
```{r}
coln <- base::c(
    "chr","start","end","cred"
  )
preAnno <- dplyr::select(preAnno_,coln)
```

## [2.3.] Annotate peaks
```{r}
postAnno <- .GlobalEnv$annotater(preAnno)
```

## [2.4.] Subset data
```{r}
preTF <- dplyr::distinct(
    .data = postAnno,
    chr,start,end,
    .keep_all = TRUE
  )
```

## [2.5.] Subset peaks for TF-association
```{r}
postTF <- preTF %>%
  dplyr::filter(
      ensembl_gene_id %in% tfs$FBgn
    ) %>%
  dplyr::mutate(
    yInj = stringr::str_replace(
        string = name,
        pattern = '^.*_(.*)$',
        replacement = '\\1'
      ),
    kclus = stringr::str_replace(
        string = name,
        pattern = '^(.*)_.*$',
        replacement = '\\1'
      )
    )
```

## [2.6.] Data wrangling
```{r}
var <- base::c(
    "chr","start","end",
    "yInj","tssChr","tssStart",
    "tssEnd","tssStrand","ensembl_gene_id",
    "external_gene_name","kclus"
  )

sortTF <- postTF %>%
  dplyr::select(!!!var) %>% 
  dplyr::mutate(
      yInj = base::as.integer(yInj),
      kclus = base::as.integer(kclus)
    ) %>% 
  dplyr::arrange(yInj)
```

## [2.7.] TFs identified to be expressed in INPs according to scRNASeq
#### see [8.4.] in 'scRNAseq_analysis.Rmd'
```{r}
clus <- base::list()
clus[[2]] <- base::c(
    "dpn","ase","cas",
    "E(spl)mbeta-HLH","slp2","aop",
    "mip120","opa","Optix",
    "crol","zfh2","jumu",
    "Oli","lilli","Mad"
  )
clus[[3]] <- base::c(
    "su(Hw)","Rbf","hth",
    "Lim1","phol","Eip75B",
    "ph-p","hng1","bigmax",
    "MTA1-like","sna","E(bx)",
    "lilli","SoxN","mod",
    "apt","zfh2","E2f1",
    "Su(var)2-10","ktub","lid",
    "Optix"
  )
clus[[4]] <- base::c(
    "Pep","ham","lilli",
    "hng3","slp2","ewg",
    "noc","Myb","Smox",
    "zfh2","crp","Hsf",
    "Eip75B","hth","apt",
    "SoxN","pros","Su(var)205",
    "klu","sd","corto"
  )
clus[[5]] <- base::c(
    "ey","fd102C","Gug",
    "Su(H)","Psc","Eip75B",
    "ham","crp","Lim1",
    "BEAF-32","opa","crc",
    "run","E2f1","Mnt","scro",
    "hng3","zfh2"
  )
clus[[6]] <- base::c(
    "hth","aop","run",
    "stwl","Lim1","trx",
    "Eip75B","sd","Optix",
    "apt","ham","corto",
    "ey","ph-p","Gug",
    "E2f1","pros","D",
    "slp2","E(spl)m8-HLH","hbn",
    "tap","SoxN","HmgZ",
    "CrebA","scrt","noc",
    "wor","klu","emc",
    "opa"
  )
```

## [2.8.] Save sortTF
#### see [7.0.] in '20190424_workflow_clustering.Rmd'
```{r}
seed = 0L #1L
base::set.seed(seed)
clusChos = 6L #5L
algr = "Hartigan-Wong"

base::saveRDS(
    object = sortTF,
    file = base::paste0(
       here::here("data//"),
      base::format(base::Sys.time(), "%Y%m%d"),
      "_sortTF_DichaeteOnly_zscores",
      "_FDR", FDR,
      "_clus", clusChos,
      "_algr", stringr::str_replace(algr, "-",""),
      "_seed", seed,
      ".rds"
    ),
    compress = TRUE
  )
```

## [2.9.] Evaluation
#### Sum amount of TF-associated peaks per cluster
```{r}
sortTF %>%
  dplyr::group_by(kclus) %>%
  dplyr::summarise(
      amount = dplyr::n()
    )

sortTF %>%
  dplyr::filter(
      external_gene_name %in% base::c("scro","hbn")
    )
```

## [2.10.] Combine resKclus & sortTF
#### previous: 'dplyr::select(2:4,7:13)'
```{r}
vars <- dplyr::vars(
    "chr","start","end","kclus",
    tidyselect::contains("Dichaete")
  )

mergeTF <- resKclus %>%
  dplyr::select(!!!vars) %>%
  dplyr::left_join(
      x = sortTF,
      y = .,
      by = base::c("chr","start","end","kclus"),
      all.x = TRUE
    ) %>%
  dplyr::arrange(yInj)
```

## [2.11.] Save mergeTF object
```{r}
seed = 0L #1L
base::set.seed(seed)
clusChos = 6L #5L
algr = "Hartigan-Wong"

base::saveRDS(
    object = mergeTF,
    file = base::paste0(
        here::here("data/"),
        base::format(base::Sys.time(), "%Y%m%d"),
        "_postAnno",
        "_mergeTF",
        "_FDR", FDR,
        "_clus", clusChos,
        "_algr", stringr::str_replace(algr, "-",""),
        "_seed", seed,
        "_all",
        ".rds"
      ),
    compress = TRUE
  )
```

## [2.12.] Prepare data for plotting
```{r}
plotTF_ <- mergeTF %>%
  tidyr::gather(
      key = "track",
      value = "bindInt",
      -chr, -start, -end,
      -kclus, -yInj, -tssChr,
      -tssStart, -tssEnd, -tssStrand,
      -ensembl_gene_id,
      -external_gene_name,
    ) %>%
  dplyr::mutate(
    track = base::factor(
        x = track,
        levels = repl$profile,
        ordered = TRUE
      ),
    chr = base::factor(
        x = chr,
        levels = sel_chrom,
        ordered = TRUE
      ),
    id = stringr::str_c(
        chr,start,end,sep="_"
      ),
    sym = purrr::map_chr(
      .x = track,
      .f = function(tr){
        return(
          repl %>%
            dplyr::filter(profile==tr) %>%
            dplyr::pull(sym)
          )
        }
      ),
    sym = base::factor(
        x = sym,
        levels = repl$sym,
        ordered = TRUE
      )
    ) %>%
  dplyr::arrange(chr,start,sym)

idLevels <- plotTF_ %>%
  dplyr::distinct(id) %>%
  dplyr::pull(id)

plotTF <- plotTF_ %>%
  dplyr::mutate(
    id = base::factor(
      x = id,
      levels = idLevels,
      ordered = TRUE
    )
  )

# rangE <- plotTF %$%
#   range(bindInt)
rangE <- base::c(-2,2)
```

## [2.13.] Evaluation
```{r}
plotTF %>%
  dplyr::filter(
      external_gene_name %in% base::c("scro","grh","hbn")
    )
```

## [2.14.] Data visualization
```{r}
FDR = 25L
seed = 0L

for(i in base::seq(1L,6L,1L)){
  
    tmp <- dplyr::filter(plotTF,kclus==i)
    
    y_labels <- tmp %>%
      dplyr::distinct(id, .keep_all = TRUE) %>% 
      dplyr::select(external_gene_name) %>%
      dplyr::pull(external_gene_name)
  
    plot_out <- ggplot2::ggplot(
          data = tmp,
          mapping = aes(
            x = sym,
            y = id,
            fill = bindInt
          )
        ) +
      geom_tile(
          height = 0.85,
          width = 0.9,
          colour = "black"
        )  +
      scale_y_discrete(
          labels = y_labels
        ) +
      scale_fill_gradient2(
          limits = base::c(rangE[1],rangE[2]),
          low = "darkblue",
          mid = "white",
          high = "darkred"
        ) +
      theme_bw() +
      theme(
          axis.text.x = element_text(
            angle = 90,
            vjust = 0.5,
            hjust = 1
          ),
          axis.text.y = element_text(
            size = 4
          ),
          axis.title = element_blank(),
          aspect.ratio = 8
        )
    
    for(ext in base::c("pdf", "png")){
        ggplot2::ggsave(
          filename = base::paste0(
              here::here("results/20181205_NanoDam_DichaeteOgre_GrhEyD/"),
              base::format(base::Sys.time(), "%Y%m%d"),
              "_plotTF_heatmap",
              "_FDR", FDR,
              "_clus", clusChos,
              "_algr", stringr::str_replace(algr, "-",""),
              "_seed", seed,
              "_kclus", i,
              ".", ext
            ),
          plot = plot_out,
          device = ext,
          dpi = 300,
          width = 4,
          height = 6
        )
      }
    
    base::print(plot_out)
  }
```

##--------------------------##
##----Print_entire_preTF----##
##--------------------------##

## [3.0.] Prepare data for writing
```{r}
vars <- base::c(
    peakChr = "chr",
    peakStart = "start",
    peakEnd = "end"
  )

writeList <- preTF %>%
  dplyr::rename(.,!!!vars) %>%
  dplyr::mutate(
    kclus = stringr::str_replace(
        string = name,
        pattern = '^(.*)_.*$',
        replacement = '\\1'
      ),
    yInj = stringr::str_replace(
        string = name,
        pattern = '^.*_(.*)$',
        replacement = '\\1'
      )
    ) %>%
  dplyr::select(-name,-nd) %>%
  dplyr::arrange(
      kclus,peakChr,peakStart
    ) %>%
  dplyr::select(12,1:11,13)
```

## [3.1.] Write data out
```{r}
utils::write.table(
    x = writeList,
    file =  base::paste0(
        here::here("results//"),
        base::format(base::Sys.time(), "%Y%m%d"),
        "_postAnno",
        "_preTF",
        "_FDR", FDR,
        "_clus", clusChos,
        "_algr", stringr::str_replace(algr, "-",""),
        "_seed", seed,
        ".tsv"
      ),
    quote = FALSE,
    sep = "\t",
    eol = "\n",
    row.names = FALSE,
    col.names = TRUE
  )
```
