---
title: "20190424_workflow_clustering"
author: "R_Krautz"
date: "05/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## [-1.0.] Install necessary packages
```{r}
utils::install.packages("adegenet")
BiocManager::install("BSgenome.Dmelanogaster.UCSC.dm6")
devtools::install_github('VPetukhov/ggrastr')
```

## [0.0.] Load necessary libraries
```{r message=FALSE}
base::library(tidyverse)
base::library(magrittr)
base::library(ggrastr)
base::library(here)
base::library(bedr)

base::library(rtracklayer)
base::library(IRanges)
base::library(UpSetR)
base::library(cluster)
base::library(mclust)
base::library(factoextra)

base::library(BSgenome)
base::library(BSgenome.Dmelanogaster.UCSC.dm6)

base::library(doParallel)
base::library(foreach)
doParallel::registerDoParallel(cores = 40)

##<<necessary?_start>>
#base::library(adegenet)
#base::library(Rtsne)
##<<necessary?_end>>
```

## [0.1.] Save & load image
```{r}
base::save.image(
   file = base::paste0(
        here::here("data/20181205_NanoDam_DichaeteOgre_GrhEyD_peaks/"),
        "20211126_rerun.RData"
      ),
   compress = TRUE
  )
```

```{r}
base::load(
   file = base::paste0(
      here::here("data/20181205_NanoDam_DichaeteOgre_GrhEyD_peaks/"),
      "20211126_rerun.RData"
    )
  )
```

##---------------------##
##----Prerequisites----##
##---------------------##

## [0.1.] All prerequisites
```{r}
FDRs <- base::c(
    2000L, 1900L, 1800L, 1700L, 1600L, 1500L, 1400L, 1300L,
    1200L, 1100L, 1000L, 900L, 800L, 700L, 600L, 500L,  
    475L, 450L, 425L, 400L, 375L, 350L, 325L, 300L,
    275L, 250L, 225L, 200L, 175L, 150L, 125L, 100L,
    75L, 50L, 25L, 10L, 5L, 3L, 2L, 1L, 0L
  )
sel_chrom <- base::c(
    "2L", "2R", "3L",
    "3R", "4","MT",
    "X", "Y"
  )

cols3 <- base::c(
    "#ED4938","#ADC607","#F4C10D",
    "#333136", "#687BC0","#E76F99",
    "#ED9038", "#2AB348", "#106881",
    "#4113CB"
  )
```

## [0.2.] Experimental groups
```{r}
groups <- tibble::tibble(
  profile = base::c(
      "DichaeteGal4_DichaeteGFP",
      "DichaeteGal4_GrainyheadGFP",
      "DichaeteGal4_EyelessGFP",
      "OgreGal4_DichaeteGFP",
      "OgreGal4_EyelessGFP"
    )
  )
```

##------------------------------##
##----Components_of_workflow----##
##------------------------------##

## [1.0.] filer() function to identify files of interest
```{r}
filer <- function(fdr, dir = folder){
  return(
    base::list.files(
        path = dir,
        full.names = TRUE
      ) %>%
    stringr::str_subset('reproPeak') %>%
    stringr::str_subset(
     base::paste0('._',fdr,'\\..*')
    )
  )
}
```

## [1.1.] reader() function
```{r}
reader <- function(filename, fdr = 25L, chroms = sel_chrom){
  return(
    readr::read_delim(
        file = filename,
        delim = "\t",
        quote = "",
        col_names = base::c(
            "chr","start","end","sign"
          ),
        col_types = "ciic"
      ) %>%
    dplyr::mutate(
      chr = base::factor(
          x = chr,
          levels = chroms,
          ordered = TRUE
        ),
      sign = stringr::str_replace(
          string  = sign,
          pattern = base::paste0('(.*)_',fdr,'\\.repro.*$'),
          replacement = '\\1'
        )
      )
    )
  }
```

## [1.2.] merger() function to reduce peaks bedr-dependent
```{r}
merger <- function(df, chosenEngine="bedtools"){
  
  out <- tryCatch(
      {
        if(!bedr::check.binary(chosenEngine)){
          stop(
           base::paste0(
              "Chosen engine:\t",chosenEngine,"\tnot available.\n"
             )
          )
        }else{
          
          is.df.valid <- df %>%
            base::as.data.frame() %>%
            bedr::is.valid.region(
                check.chr = FALSE
              )
          
          dfVal <- df %>%
            dplyr::filter(
                dplyr::row_number() == base::which(is.df.valid)
              ) %>% 
            base::as.data.frame()
          
          dfSort <- bedr::bedr(
              engine = chosenEngine,
              input = base::list(i=dfVal),
              method = "sort",
              params = "",
              check.chr = FALSE,
              check.valid = TRUE,
              check.sort = FALSE
            )
          
          dfMerg <- bedr::bedr(
              engine = chosenEngine,
              input = base::list(i=dfSort),
              method = "merge",
              params = "-c 4 -o distinct",
              check.chr = FALSE,
              check.valid = TRUE,
              check.sort = TRUE,
              check.merge = FALSE
            )
          
          dfMerg %>%
            tibble::as_tibble() %>%
            dplyr::arrange(chr, start)
          
        }
    },
    error = function(cond){
        base::message(cond)
        return(NA)
      },
    warning = function(cond){
        base::message(cond)
        return(NA)
      }
    )
  return(out)  
  }
```

## [1.3.] cluster() function for cluster assignment
```{r}
cluster <- function(df, groups=groups){

  lookup <- df %>%
    dplyr::distinct(sign) %>%
    dplyr::mutate(
        clus = dplyr::row_number()
      )
  
  return(
    df %>%
      dplyr::mutate(
        peak = stringr::str_split(
            sign,
            pattern = ","
          ),
        clus = purrr::map_int(
          .x = sign,
          .f = function(x){
            return(
              lookup %>%
                dplyr::filter(
                    sign == x 
                  ) %>%
                dplyr::select(clus) %>%
                base::unlist() %>%
                base::unname()
              )
            }
          ),
        coord = purrr::pmap_chr(
            .l = base::list(
                chr,start,end
              ),
            .f = stringr::str_c,
            sep = "_"
          ),
        data = purrr::map(
          .x = peak,
          .f = function(x){
            return(
              groups %>%
                dplyr::mutate(
                  present = dplyr::case_when(
                      profile %in% base::as.character(x) ~ 1L,
                      TRUE ~ 0L
                    )
                  )
              )
            }
          )
        ) %>%
      tidyr::unnest(cols = "data") %>%
      dplyr::arrange(clus,chr,start)
    )
  }
```

##----------------##
##----Analysis----##
##----------------##

## [2.0.] Read in & aggregate
```{r}
FDR = 25L

files <- .GlobalEnv$filer(
      fdr= FDR,
      dir = here::here("data/20181205_NanoDam_DichaeteOgre_GrhEyD_peaks")
    ) %>%
  stringr::str_subset('DichaeteGal4_')

preMerge <- purrr::map_dfr(
      .x = files,
      .f = .GlobalEnv$reader,
      fdr = FDR
    ) %>%
  dplyr::arrange(chr, start) %>% 
  dplyr::mutate(
      chr = base::as.character(chr)
    )
```

## [2.1.] Evaluate read datasets
```{r}
preMerge %>%
  dplyr::group_by(sign,chr) %>%
  dplyr::summarise(amount = dplyr::n())
```

## [2.2.] Apply merger() & cluster()
```{r}
groups_ <- groups %>%
  dplyr::filter(
      stringr::str_detect(profile,"^Dichaete")
    )

postMerge <- .GlobalEnv$merger(df = preMerge)
postClus <- .GlobalEnv$cluster(
    df = postMerge,
    groups = groups_
  )
```

## [3.0.] Data preparation for heatmap visualization
```{r}
lev <- postClus %>%
  dplyr::distinct(coord) %>%
  dplyr::pull(coord)

subset <- postClus %>%
   dplyr::arrange(clus,chr,start) %>%
    dplyr::mutate(
      coord = base::factor(
        x = coord,
        levels = lev,
        ordered = TRUE
      )
    )
```

## [3.1.] Data visualization via heatmaps
```{r}
plot <- ggplot2::ggplot(
      data = subset,
      mapping = aes(
        x = profile,
        y = coord,
        fill = present
      )
    ) +
  ggrastr::geom_tile_rast() +
  scale_fill_gradient2(
      low = "white",
      high = "darkred"
    ) +
  theme(
    axis.title = element_blank(),
    axis.text.x = element_text(
        angle = 90,
        vjust = 0.5,
        hjust = 1,
        size = 12
      ),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "none",
    aspect.ratio = 3,
    panel.border = element_rect(
        color = "black",
        fill=NA,
        size=1
      )
    )

base::print(plot)
```

## [3.2.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
    ggplot2::ggsave(
      filename = base::paste0(
          here::here("results/20181205_NanoDam_DichaeteOgre_GrhEyD/"),
          base::format(base::Sys.time(), "%Y%m%d"),
          "_heatmap_binaryPeakAppearance_FDR", FDR,
          "_DichOgre",
          ".", ext
        ),
      plot = plot,
      device = ext,
      dpi = 300,
      width = 3,
      height = 8
    )
  }
```

## [3.3.] Data preparation for UpSetR plot
```{r}
upSubset <- postClus %>%
  dplyr::select(coord,profile,present) %>%
  tidyr::spread(
      key = "profile",
      value = "present"
    ) %>%
  base::as.data.frame()
```

## [3.4.] UpSetR plot visualization
```{r}
UpSetR::upset(
    data = upSubset,
    sets = dplyr::pull(groups_,profile),
    nintersects = NA,
    sets.bar.color = "darkred",
    order.by = "freq",
    empty.intersections = "on",
    keep.order = TRUE,
    show_numbers
  )
```

## [3.5.] Save plot
```{r}
outfile <- base::paste0(
    here::here("results/20181205_NanoDam_DichaeteOgre_GrhEyD/"),
    base::format(base::Sys.time(), "%Y%m%d"),
    "_UpSetR_binaryPeakAppearance_FDR", FDR,
    "_DicOgre.pdf"
  )

grDevices::pdf(
  outfile,
  width = 10,
  height = 5,
  onefile = FALSE
  )
base::print(
  UpSetR::upset(
      data = upSubset,
      sets = dplyr::pull(groups_,profile),
      nintersects = NA,
      sets.bar.color = "darkred",
      order.by = "freq",
      empty.intersections = "on",
      keep.order = TRUE,
      show.numbers = FALSE
    )
  )
grDevices::dev.off()
```

##----------------------##
##-----DamID_scores-----##
##----------------------##

## [4.0.] Function to read in all *.quant.norm.bedgraph files
```{r}
reader <- function(fn, chroms = sel_chrom, regex='^.*/(.*?)\\.gatc.*$'){
    
    sample <- stringr::str_replace(fn, regex, '\\1')
    
    file <- readr::read_delim(
          file = fn,
          delim = '\t',
          col_types = "ciin",
          col_names = base::c(
              'chr','start','end','score'
            )
        )  %>%
      dplyr::filter(chr %in% chroms) %>%
      dplyr::mutate(
          chr = stringr::str_replace(chr, "^chr", ""),
          name = sample
        )
    return(file)
  }
```

## [4.1.] Aggregate function
#### additional summary function 'sumabs = base::sum(int_score)'
```{r}
aggregator <- function(chr,start,end,agg,...){
  return(
    agg %>%
      dplyr::rename(.,x=chr,y=start,z=end) %>% 
      dplyr::filter(x==chr) %>%
      dplyr::filter(!(z<=start | y>=end)) %>%
      dplyr::mutate(
           y = base::ifelse(
              test = y<start,
              yes = start,
              no = y
            ),
          z = base::ifelse(
              test = z>end,
              yes = end,
              no = z
            ),
          int_score = (score*(z-y))
        ) %>%
      dplyr::group_by(name) %>%
      dplyr::summarise(
        sum = base::sum(int_score)/(end-start)
      )
    )
  }
```

## [5.0.] Identify files
#### Note: Negative lookahead used in str_subset()
#### Note: Previous folder 'data/20181012_phes5Flox2_cux2Fezf2Pou3f2_tracks'
#### files: "DichaeteGal4_DichaeteGFP_vs_DichaeteGal4_w1118.bedgraph"; "DichaeteGal4_EyelessGFP_vs_DichaeteGal4_w1118.bedgraph" etc.
```{r}
files <- base::list.files(
      path = here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks"),
      full.names = TRUE
    ) %>%
  stringr::str_subset('quant.norm.bedgraph$') %>%
  stringr::str_subset('^(?!.*unlogged)') %>%
  stringr::str_subset('DichaeteGal4_')
```

## [5.1.] Read in all scores of all files 
```{r}
agg <- purrr::map_dfr(
    .x= files,
    .f = .GlobalEnv$reader,
    regex = '^.*/(.*?_.*?)_.*$'
  )
```

## [5.2.] Save & load agg
```{r}
base::saveRDS(
    object = agg,
    file = base::paste0(
        here::here("data/20190901_DichaeteGal4_DGrhEy_clustering/"),
        base::format(base::Sys.time(), "%Y%m%d"),
        "_agg",
        "_FDR", FDR,
        ".rds"
      ),
    compress = TRUE
  )
```

```{r}
agg <- base::readRDS(
  file = list.files(
        here::here("data/20190901_DichaeteGal4_DGrhEy_clustering"),
        full.names = TRUE
      ) %>%
    stringr::str_subset("_agg")
  )
```

## [5.3.] Transform scores into unlogged state
```{r}
agg_unlog <- dplyr::mutate(
    .data = agg,
    score = 2^score
  )
```

## [5.4.] Apply aggregator() on tester peak set
```{r}
base::set.seed(0)
tester <- dplyr::slice_sample(postClus, n = 10)

res <- tester %>% 
  dplyr::mutate(
    scores = purrr::pmap(
      .l = base::list(
            chr,start,end
          ),
      .f = .GlobalEnv$aggregator,
      agg = .GlobalEnv$agg
      )
    ) %>%
  tidyr::unnest(
      cols = "scores"
    ) %>%
  tidyr::spread(
      key = "name",
      value = "sum"
    )
```

## [5.5.] Apply aggregator() on entire postClus dataset
#### Note: previous specifications 'agg = .GlobalEnv$agg_unlog'
```{r}
var = base::c(
    "chr","start","end","sign","clus"
  )
res <- postClus %>%
  dplyr::distinct(!!!rlang::syms(var)) %>%
  dplyr::mutate(
      scores = purrr::pmap(
        .l = base::list(
            chr,start,end
          ),
        .f = .GlobalEnv$aggregator,
        agg = .GlobalEnv$agg
      )
    ) %>%
  tidyr::unnest(
      cols = "scores"
    ) %>%
  tidyr::spread(
      key = "name",
      value = "sum"
    )
```

## [5.6.] Parallel implementation of aggregator()
#### 'dplyr::filter_all(preAgg,dplyr::all_vars(is.na(.))); 'dplyr::distinct(preAgg,sign)'; 'dplyr::distinct(res,sign)'
```{r}
preAgg <- dplyr::distinct(postClus,!!!rlang::syms(var))

res <- foreach::foreach(i = 1:base::nrow(preAgg)) %dopar% {
      preAgg %>%
        dplyr::filter(dplyr::row_number() == i) %>%
        dplyr::mutate(
        scores = purrr::pmap(
          .l = base::list(
              chr,start,end
            ),
          .f = .GlobalEnv$aggregator,
          agg = .GlobalEnv$agg
        )
      ) %>%
      tidyr::unnest(
          cols = "scores"
        ) %>%
      tidyr::spread(
          key = "name",
          value = "sum"
        )
    } %>%
  dplyr::bind_rows(.)
```

## [5.7.] Save & load res for unlogged data
#### 'res' is 'postAgg' in other workflows
```{r}
base::saveRDS(
    object = res,
    file = base::paste0(
        here::here("data/20190901_DichaeteGal4_DGrhEy_clustering/"),
        base::format(base::Sys.time(), "%Y%m%d"),
        "_res",
        "_FDR", FDR,
        ".rds"
      ),
    compress = TRUE
  )
```

```{r}
res <- base::readRDS(
  file = base::list.files(
        here::here("data/20190901_DichaeteGal4_DGrhEy_clustering"),
        full.names = TRUE
      ) %>%
    stringr::str_subset('_res_')
  )
```

##-------------------------##
##----kmeans_clustering----##
##-------------------------##

## [5.8.] Data wrangling
#### Note: Include scale() to normalize variables
```{r}
groupsCur <- dplyr::pull(groups_,profile)

resClus_ <- res %>%
  dplyr::mutate(
    id = stringr::str_c(
      chr,start,end,sign,clus,
      sep = "_"
      )
    ) %>%
  base::as.data.frame()%>% 
  tibble::column_to_rownames(.,var = "id") %>%
  dplyr::select(!!groupsCur) %>%
  stats::na.omit() %>%
  base::scale()

##Remove attributes
##-----------------
resClus <- resClus_[,]
base::dim(resClus_)
resClus[1:5,1:base::ncol(resClus)]
```

## [5.9.] Evaluate normalization into z-scores
```{r}
resClus %>%
  base::as.data.frame() %>%
  dplyr::summarise_each(
    funs = dplyr::funs(
        mean = mean,
        sd = sd
      )
    ) %>%
  tidyr::gather(
      key = "comb",
      value = "value"
    ) %>%
  dplyr::mutate(
    param = stringr::str_replace(
        string = comb,
        pattern = '.*_.*_(.*)',
        replacement = '\\1'
      ),
    group = stringr::str_replace(
        string = comb,
        pattern = '(.*_.*)_.*',
        replacement = '\\1'
      )
    ) %>%
  dplyr::select(2:4) %>% 
  tidyr::spread(
      key = "param",
      value = "value"
    )
```

## [5.10.] Save & load scaled resClus
```{r}
base::saveRDS(
    object = resClus,
    file = base::paste0(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/"),
        base::format(base::Sys.time(), "%Y%m%d"),
        "_resClus_DichaeteOnly_zscores",
        "_FDR", FDR,
        ".rds"
      ),
    compress = TRUE
  )
```

```{r}
resClus <- base::readRDS(
  file = base::list.files(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/"),
        full.names = TRUE
      ) %>%
    stringr::str_subset('_resClus_')
  )
```

## [5.11.] Determine optimal amount of clusters/cluster centers
```{r}
seed = 0L
base::set.seed(seed)

factoextra::fviz_nbclust(
    x = resClus, 
    FUNcluster = kmeans,
    method = "gap_stat"
  )
```

##<<necessary?_start>>

## [5.12.] Save plot
```{r}
outfile <- base::paste0(
    here::here("results/20190901_DichaeteGal4_DGrhEy_clustering/"),
    base::format(base::Sys.time(), "%Y%m%d"),
    "_resClus",
    "_NrClusters",
    "_FDR", FDR,
    "_seed", seed,
    ".pdf"
  )

grDevices::pdf(
    outfile,
    ".pdf",
    width = 5,
    height = 5
  )
base::print(
    factoextra::fviz_nbclust(
      x = resClus, 
      FUNcluster = kmeans,
      method = "gap_stat"
    )
  )
grDevices::dev.off()
```

##<<necessary?_end>>

## [5.13.] clValid dependent validation of clusters
```{r}
clusVal <- clValid::clValid(
    obj = base::as.matrix(resClus),
    nClust = base::seq(2,9,1),
    clMethods = base::c("hierachical", "kmeans", "pam"),
    validation = base::c("internal", "stability")
  )
clValid::summary(clusVal)
```

##<<necessary?_start>>

## [5.14.] Save & load clValid-summary
```{r}
base::saveRDS(
    object = clusVal,
    file = base::paste0(
      here::here("data/20190901_DichaeteGal4_DGrhEy_clustering/"),
      base::format(base::Sys.time(), "%Y%m%d"),
      "_clusVal",
      "_FDR", FDR,
      "_seed", seed,
      ".rds"
      ),
    compress = TRUE
  )
```

```{r}
clusVal <- base::readRDS(
    file = list.files(
        here::here("data/20190901_DichaeteGal4_DGrhEy_clustering"),
        full.names = TRUE
      ) %>%
    stringr::str_subset('clusVal')
  )
```

##<<necessary?_end>>

## [5.15.] Bayesian information criterion for expectation maximization
##<<necessary?_start>>
#### Note: 'scale(motifClus)' and 'motifClus' represented by 18 clusters
##<<necessary?_end>>
```{r}
base::set.seed(0)
tmp <- mclust::Mclust(
  data = base::as.matrix(resClus),
  G = 1:20
)

base::dim(tmp$z)[2]
base::plot(tmp)
```

##-------------------------------##
##----Parallel_implementation----##
##-------------------------------##

## [6.0.] Prepare data
```{r}
preKclus <- tibble::as_tibble(
    x = resClus,
    rownames = "id"
  )
```

## [6.1.] Build 'options'-overview table
```{r}
algorithms <- base::c(
    "Hartigan-Wong", "Lloyd", "MacQueen"
  )
clusters <- base::seq(4,10,1)

options <- tibble::tibble(
    clusChos = base::sort(
        base::rep(clusters,base::length(algorithms))
      ),
    algor = base::rep(
        algorithms, base::length(clusters)
      )
    ) %>%
  dplyr::mutate(
    newData = purrr::map(
      .x = algor,
      .f = function(x){
        return(
          tibble::tibble(
              seed = base::seq(1,1000,1)
            )
          )
        }
      )
    ) %>%
  tidyr::unnest(
      cols = "newData"
    )
```

## [6.2.] Evaluate options
```{r}
options %>%
  dplyr::distinct(clusChos,seed,algor) %>%
  base::nrow()
```

## [6.3.] Run all kmeans clustering jobs parallel
```{r}
runs <- foreach::foreach(i=1:base::nrow(options), .packages = "cluster") %dopar% {
  
    df <- dplyr::filter(options,dplyr::row_number()==i)
    alg = dplyr::pull(df,algor)
    se = dplyr::pull(df,seed)
    cent = dplyr::pull(df,clusChos)
    
    base::set.seed(se)
    postKclus <- stats::kmeans(
       x =  tibble::column_to_rownames(preKclus,"id"),
       centers = cent,
       nstart = 25,
       iter.max = 1000,
       algorithm = alg
      )
    kcluster <- tibble::tibble(
        id = base::names(postKclus$cluster),
        kclus = postKclus$cluster
      )
    sil <- cluster::silhouette(
        x = dplyr::rename(kcluster, clustering = kclus),
        dist = stats::dist(preKclus)
      )
    postSil_av <- sil[,1:3] %>%
      tibble::as_tibble() %>%
      dplyr::summarise(
          mean = base::mean(sil_width)
        ) %>%
      base::unlist() %>%
      base::unname()
    
    return(
      dplyr::mutate(
          .data = df,
          meanSil = postSil_av
        )
      )
    } %>%
  dplyr::bind_rows()
```

## [6.4.] Save & load runs
```{r}
base::saveRDS(
    object = runs,
    file = base::paste0(
        here::here("data/20190901_DichaeteGal4_DGrhEy_clustering/"),
        base::format(base::Sys.time(), "%Y%m%d"),
        "_runs",
        "_FDR", FDR,
        ".rds"
      ),
    compress = TRUE
  )
```

```{r}
runs <- base::readRDS(
  file = base::list.files(
        here::here("data/20190901_DichaeteGal4_DGrhEy_clustering"),
        full.names = TRUE
      ) %>%
    stringr::str_subset('runs')
  )
```

## [6.5.] Read out optimal run
```{r}
runs %>%
  dplyr::distinct(meanSil, .keep_all = TRUE) %>%
  dplyr::arrange(dplyr::desc(meanSil))

maxSil <- runs %>%
  dplyr::summarise(max = base::max(meanSil)) %>%
  dplyr::pull(max)

runs %>%
  dplyr::filter(meanSil == maxSil)

runs %>%
  dplyr::filter(clusChos == 8L) %>%
  dplyr::arrange(dplyr::desc(meanSil))

runs %>%
  dplyr::group_by(clusChos,algor,meanSil) %>%
  dplyr::summarise(sum = dplyr::n()) %>%
  dplyr::arrange(dplyr::desc(meanSil),dplyr::desc(sum))
```

```{r}
runs %>%
  dplyr::group_by(clusChos,algor,meanSil) %>%
  dplyr::summarise(sum = dplyr::n()) %>%
  dplyr::mutate(
      comb = sum*meanSil
    ) %>% 
  dplyr::arrange(dplyr::desc(comb))

runs %>%
  dplyr::filter(
      clusChos == 5 &
      algor == "Lloyd"
    ) %>%
  dplyr::group_by(meanSil) %>%
  dplyr::summarise(sum = dplyr::n())
```

## [6.6.] Plot distribution of average silhouette widths
#### Allows to identify stable solutions
```{r}
plot <- ggplot2::ggplot(
      data = runs,
      mapping = aes(
        x = meanSil
      )
    ) +
  geom_density() +
  facet_wrap(
      facets = clusChos ~ algor,
      nrow = 1
    ) +
  scale_x_continuous(
      limits = base::c(0.18,0.27), 
      breaks = base::c(0.20,0.225,0.25)
    ) +
  theme_bw() +
  theme(
      axis.text.x = element_text(
        angle = 90,
        vjust = 0.5,
        hjust = 1
      ),
      panel.spacing = grid::unit(0.1,"lines")
    )
base::print(plot)
```

## [6.7.] Save plot
```{r}
for(ext in c("pdf", "png")){
    ggplot2::ggsave(
      filename = base::paste0(
          here::here("results/20190901_DichaeteGal4_DGrhEy_clustering/"),
          base::format(base::Sys.time(), "%Y%m%d"),
          "_runs",
          "_FDR", FDR,
          ".", ext
        ),
      plot = plot,
      device = ext,
      dpi = 300,
      width = 8,
      height = 4
    )
  }
```

##--------------------------##
##----Optimal_Clustering----##
##--------------------------##

## [5.16.] Perform clustering
##<<unnecessary_start>>
#### 'clusK' is 'kcluster' in '20181205_workflow_clustering.Rmd'
#### 'resK' is 'postKclus' in '20181205_workflow_clustering.Rmd'
##<<unnecessary_end>>
```{r}
seed = 0L
base::set.seed(seed)
clusChos = 6L
algr = "Hartigan-Wong"

resK <- stats::kmeans(
    x = resClus,
    centers = clusChos,
    nstart = 25,
    iter.max = 10000,
    algorithm = algr
  )

clusK <- tibble::tibble(
    id = base::names(resK$cluster),
    kclus = resK$cluster
  )
```

## [5.17.] Save & load resK
```{r}
base::saveRDS(
    object = resK,
    file = base::paste0(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/"),
        base::format(base::Sys.time(), "%Y%m%d"),
        "_resK_DichaeteOnly_zscores",
        "_clus", clusChos,
        "_FDR", FDR,
        "_algr", stringr::str_replace(algr, "-",""),
        "_seed", seed,
        ".rds"
      ),
    compress = TRUE
  )
```

```{r}
resK <- base::readRDS(
    file = base::list.files(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/")
      ) %>%
    stringr::str_subset('20211126_resK_')
  )
```

## [5.18.] Visualize clusters
```{r}
factoextra::fviz_cluster(
    object = resK,
    data = resClus,
    ellipse.type = "none",
    palette = "jco",
    ggtheme = ggplot2::theme_minimal(),
    labelsize = 0
  )
```

##-----------------------##
##----Silhouette_plot----##
##-----------------------##

## [6.0.] Helper functions to generate injected y column
```{r}
sequencer <- function(clus,start,end,gap=3L){
    return(
      base::seq(
        start + gap*(clus-1),
        end + gap*(clus-1)
      )
    )
  }
```

```{r}
seqAdd <- function(df, gap=30L){
  return(
    df %>%
      dplyr::mutate(
          clus = base::as.integer(clus),
          end = base::cumsum(amount),
          start = end-amount+1,
          seq = purrr::pmap(
            .l = base::list(
                clus,start,end
              ),
            .f = .GlobalEnv$sequencer,
            gap = gap
          )
        ) %>%
      tidyr::unnest(cols = "seq") %>%
      dplyr::select(seq) %>%
      base::unlist() %>%
      base::unname()
    )
  }
```

## [6.1.] Helper function for geom_rect()
```{r}
rectAdd <- function(df, gap=30L, groups=groups){
    return(
      df %>%
        dplyr::mutate(
          end = base::cumsum(amount),
          start = end-amount+1,
          startY = start+gap*(clus-1),
          endY = end+gap*(clus-1),
          startX = groups$profile[1],
          endX = groups$profile[base::nrow(groups)]
        ) %>%
      dplyr::select(1,5:8)
    )
  }
```

## [6.2.] Run silhouette function
#### evaluate with 'sil[1:5, 1:3]'
```{r}
sil <- cluster::silhouette(
    x = dplyr::rename(clusK, clustering = kclus),
    dist = stats::dist(resClus)
  )

factoextra::fviz_silhouette(sil)
```

## [6.3.] Integrate id's into silhouette results
```{r}
resSil <- sil[,1:3] %>%
  tibble::as_tibble() %>%
  dplyr::bind_cols(
      dplyr::select(clusK,id),
      .
    ) %>%
  dplyr::arrange(
      cluster, dplyr::desc(sil_width)
    )
```

## [6.4.] Save & load resSil
```{r}
base::saveRDS(
    object = resSil,
    file = base::paste0(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/"),
        base::format(base::Sys.time(), "%Y%m%d"),
        "_resSil_DichaeteOnly_zscores",
        "_clus", clusChos,
        "_FDR", FDR,
        "_algr", stringr::str_replace(algr, "-",""),
        "_seed", seed,
        ".rds"
      ),
    compress = TRUE
  )
```

```{r}
resSil <- base::readRDS(
  file = base::list.files(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/"),
        full.names = TRUE
      ) %>%
    stringr::str_subset('20190424_resSil_')
  )
```

## [6.5.] Prepare data for custome silhouette plot
```{r}
tmp <- resSil %>%
  dplyr::mutate(
    cluster = base::factor(
      x = cluster,
      levels = base::seq(1,base::nrow(resK$centers),1),
      ordered = TRUE
    )
  ) %>%
 dplyr::arrange(cluster,sil_width)

clusDis <- resSil %>%
  dplyr::group_by(cluster) %>%
  dplyr::summarise(amount = dplyr::n()) %>% 
  dplyr::rename(., clus=cluster)

tmp <- tmp %>%
  dplyr::mutate(
      yInj = .GlobalEnv$seqAdd(clusDis, gap=100L)
    ) %>%
 dplyr::arrange(yInj)

resSil_av <- sil[,1:3] %>%
  tibble::as_tibble() %>%
  dplyr::summarise(mean = base::mean(sil_width)) %>%
  base::round(.,digits = 2) %>%
  base::unlist() %>%
  base::unname()
```

## [6.6.] Plot silhouettes
```{r}
plot_sil <- ggplot2::ggplot(
      data = tmp,
      mapping = aes(
          x = yInj,
          y = sil_width,
          color = cluster,
          fill = cluster
        ),
      colour = "transparent"
    ) +
  geom_bar(
      stat = "identity"
    ) +
  geom_hline(
      yintercept = resSil_av,
      linetype = "dashed"
    ) +
  coord_flip() +
  scale_fill_manual(
      limits = base::seq(1,base::nrow(resK$centers),1),
      breaks = base::seq(1,base::nrow(resK$centers),1),
      labels = base::seq(1,base::nrow(resK$centers),1),
      values = cols3[1:nrow(resK$centers)]
    ) +
  scale_colour_manual(
      limits = base::seq(1,base::nrow(resK$centers),1),
      breaks = base::seq(1,base::nrow(resK$centers),1),
      labels = base::seq(1,base::nrow(resK$centers),1),
      values = cols3[1:nrow(resK$centers)]
    ) +
  theme_bw() +
    theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      aspect.ratio = 2,
      axis.title = element_blank()
    ) +
  guides(
    fill = guide_legend(
      label.position = "right",
      title.position = "left",
      title.theme = element_text(
        angle = 90,
        hjust = 0.5
      )
    )
  )
base::print(plot_sil)
```

## [6.7.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
    ggplot2::ggsave(
      filename = base::paste0(
          here::here("results/20181205_NanoDam_DichaeteOgre_GrhEyD/"),
          base::format(base::Sys.time(), "%Y%m%d"),
          "_silhouette_DichaeteOnly_zscores",
          "_clus", clusChos,
          "_FDR", FDR,
          "_algr", stringr::str_replace(algr, "-",""),
          "_seed", seed,
          ".", ext
        ),
      plot = plot_sil,
      device = ext,
      dpi = 300,
      width = 3,
      height = 6
    )
  }
```

##--------------------##
##----Combine_data----##
##--------------------##

## [6.8.] Include k-means cluster assignment in res
```{r}
columns_ <- base::c(
    "id","chr","start","end",
    "sign","clus","kclus"
  )
columns <- groups %>%
  dplyr::pull(profile) %>%
  stringr::str_subset('DichaeteGal4') %>%
  base::append(
      tidyselect::all_of(columns_),.
    )

resKclus_ <- res %>%
  dplyr::mutate(
      id = stringr::str_c(
        chr,start,end,sign,clus,
        sep = "_"
      )
    ) %>%
  dplyr::left_join(
      x = .,
      y = clusK,
      by = "id"
    ) %>%
  dplyr::arrange(kclus) %>% 
  dplyr::select(columns)
```

## [6.9.] Include resSil cluster positions
```{r}
resKclus <- dplyr::left_join(
    x = resKclus_,
    y = dplyr::select(resSil,id,sil_width),
    by = "id"
  )
```

## [6.10.] Save & load resKclus
```{r}
base::saveRDS(
    object = resKclus,
    file = base::paste0(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/"),
        base::format(base::Sys.time(), "%Y%m%d"),
        "_resKclus_DichaeteOnly_zscores",
        "_clus", clusChos,
        "_FDR", FDR,
        "_algr", stringr::str_replace(algr, "-",""),
        "_seed", seed,
        ".rds"
      ),
    compress = TRUE
  )
```

```{r}
resKclus <- base::readRDS(
  file = base::list.files(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/")
      ) %>%
    stringr::str_subset('20211126_resKclus_')
  )
```

```{r}
utils::write.table(
    x = resKclus,
    file = base::paste0(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/"),
        base::format(base::Sys.time(), "%Y%m%d"),
        "_resKclus_DichaeteOnly_zscores",
        "_clus", clusChos,
        "_FDR", FDR,
        "_algr", stringr::str_replace(algr, "-",""),
        "_seed", seed,
        ".tsv"
      ),
    sep = "\t",
    eol = "\n",
    col.names = TRUE,
    row.names = FALSE,
    quote = FALSE
  )
```

##-----------------------##
##----Write_bed_files----##
##-----------------------##

## [6.11.] Write_out_bed_files
```{r}
coln <- base::c(
    "chr","start","end",
    "name","score","strand",
    "thickStart","thickEnd","color"
  )
chroms <- sel_chrom %>%
  purrr::discard(.,~.x=="MT") %>%
  base::paste0("chr",.)

res_bed <- resKclus %>%
  dplyr::mutate(
    chr = stringr::str_c("chr",chr),
    chr = base::factor(
        x = chr,
        levels = chroms,
        ordered = TRUE
      ),
    name = purrr::pmap_chr(
        .l = base::list(
            kclus,sign
          ),
        .f = stringr::str_c,
        sep = "_"
      ),
    score = "0",
    strand = "*",
    thickStart = start,
    thickEnd = end,
    color = purrr::map_chr(
        .x = kclus,
        .f = ~ cols3[.x]
      )
    ) %>%
  dplyr::select(tidyselect::all_of(coln)) %>%
  dplyr::arrange(chr,start,end)
```

## [6.12.] Evaluate res_bed
```{r}
dplyr::distinct(res_bed,name,color)
```

## [6.13.] Write out res_bed
```{r}
trackline <- base::paste(
    "track name=\"FDR150_seed0\"",
    "description=\"FDR150_seed0\"",
    "visibility=2",
    "itemRgb=\"On\"",
    sep = "\t"
  )

fn <- base::paste0(
    here::here("data/20190901_DichaeteGal4_DGrhEy_clustering/"),
    "Dichaete_comKclus",
    "_FDR", FDR,
    "_clus", clusChos,
    "_algr", stringr::str_replace(algr, "-",""),
    "_seed", seed,
    ".reproPeak.bed"
  )

utils::write.table(
    x = trackline,
    file = fn,
    sep = "\n",
    eol = "\n",
    row.names = FALSE,
    col.names = FALSE,
    qmethod = "escape",
    quote = FALSE
  )

utils::write.table(
    x = res_bed,
    file = fn,
    sep = "\t",
    eol = "\n",
    row.names = FALSE,
    col.names = FALSE,
    qmethod = "escape",
    quote = FALSE,
    append = TRUE
  )
```

##<<unnecessary_start>>

##--------------------##
##----PCA_Analysis----##
##--------------------##

## [5.21.] PCA analysis
##### Note: 'factoextra::fviz_pca_ind(pca,label = "none",habillage = res_mclus$Mclus)'
```{r}
pca <- stats::prcomp(
    x = resKclus %>%
     dplyr::arrange(clus,chr,start) %>% 
      dplyr::select(!!groups$profile)
  )

pca_sum <- factoextra::facto_summarize(
    X = pca,
    element = "ind",
    axes = base::c(1,2,3,4),
    result =  base::c("coord", "contrib", "cos2")
  )

pca_contr <- factoextra::facto_summarize(
    X = pca,
    element = "var",
    axes = base::c(1,2,3,4),
    result =  base::c("coord", "contrib", "cos2")
  )

res_pca <- resKclus %>%
 dplyr::arrange(clus,chr,start) %>%
  cbind(.,pca_sum) %>%
  dplyr::mutate(
    kclus = base::factor(
      kclus,
      levels = base::seq(1, nrow(resK$centers), 1),
      ordered = TRUE
    )
  ) %>%
 dplyr::arrange(kclus)
```

## [5.22.] Save resKclus
```{r}
base::saveRDS(
  object = res_pca,
  file = here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/20181207_res_pca_FDR25_seed0_k9_zscores.rds"),
  compress = TRUE
)
```

## [5.23.] Load resKclus
```{r}
res_pca <- base::readRDS(
    file =  here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/20181207_res_pca_FDR25_seed0_k9_zscores.rds")
  )
```

## [5.18.] Helper function huller() for convex hulls
##### Note: reduce hulls by 'res_pca %>% dplyr::filter(Dim.3 <= 4L & Dim.3 >=-4L)'
```{r}
dimX = 1L
dimY = 2L
colX <-base::paste0("Dim.",dimX)
colY <-base::paste0("Dim.",dimY)

huller <- function(df){
    df[grDevices::chull(df[,colX],df[,colY]),]
  } 

hulls <- plyr::ddply(res_pca,"kclus",huller)
```

## [5.19.] Print pca plot with convex hulls
```{r}
 plot_pca <- ggplot2::ggplot() +
  geom_point(
    data = res_pca,
    aes(
      x=res_pca[,colX],
      y=res_pca[,colY],
      fill = kclus
    ),
    alpha=0.6,
    colour="black",
    pch = 21,
    stroke = 0.1
  ) +
  geom_hline(
    yintercept = 0,
    linetype = "dashed"
  ) +
  geom_vline(
    xintercept = 0,
    linetype = "dashed"
  ) +
  geom_polygon(
    data = hulls,
    aes(
      x=hulls[,colX],
      y=hulls[,colY],
      fill = kclus,
      colour = kclus
    ),
    alpha = 0.15
  ) +
  scale_fill_manual(
    limits = base::seq(1,base::nrow(resK$centers),1),
    breaks = base::seq(1,base::nrow(resK$centers),1),
    labels = base::seq(1,base::nrow(resK$centers),1),
    values = cols3[1:nrow(resK$centers)],
    guide = guide_legend(
      label.position = "right",
      title.position = "left",
      direction = "vertical",
      title.theme = element_text(
        angle = 90,
        hjust = 0.5
      )
    )
  ) +
  scale_colour_manual(
    limits = base::seq(1,base::nrow(resK$centers),1),
    breaks = base::seq(1,base::nrow(resK$centers),1),
    labels = base::seq(1,base::nrow(resK$centers),1),
    values = cols3[1:nrow(resK$centers)],
    guide = "none"
  ) +
  theme(
    legend.position = "right"
  )

base::print(plot_pca)
```

## [5.20.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
  ggplot2::ggsave(
    filename = base::paste0(
      here::here("results/20181205_NanoDam_DichaeteOgre_GrhEyD/20181207_pcaCustome_FDR25_seed0_DichOgre_"),
      "Dim", dimX, "_",
      "Dim", dimY, "_",
      "k", nrow(resK$centers),
      "_zscores.",
      ext
    ),
    plot = plot_pca,
    device = ext,
    dpi = 300,
    width = 6,
    height = 4
  )
}
```

##<<unnecessary_end>>

##-----------------------------##
##----Cluster_visualization----##
##-----------------------------##

## [7.0.] Load resKclus
```{r}
resKclus <- base::readRDS(
  file = base::list.files(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/")
      ) %>%
    stringr::str_subset('_resKclus')
  )
```

## [7.1.] Load resK
```{r}
resK <- base::readRDS(
  file = base::list.files(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/")
      ) %>%
    stringr::str_subset('_resK_')
  )
```

## [7.2.] Prepare for visualization
##### Note: generate 'idLevels' vector by 'tmp %>% dplyr::group_by(id) %>% distinct(id) %>% base::unlist() %>% base::unname()'
```{r}
tmp <- resKclus %>%
dplyr::as_tibble() %>% 
  dplyr::mutate(
      kclus = base::factor(
        x = kclus,
        levels = base::seq(1,base::nrow(resK$centers)),
        ordered = TRUE
      )
    ) %>%
  dplyr::arrange(kclus,sil_width)

clusDis <- resKclus %>%
  dplyr::group_by(kclus) %>%
  dplyr::summarise(amount = dplyr::n()) %>% 
  dplyr::rename(., clus = kclus)

tracks <- dplyr::pull(groups_,profile)

resViz <- tmp %>%
  dplyr::mutate(
      yInj = .GlobalEnv$seqAdd(clusDis, gap=100L)
    ) %>%
  tidyr::gather(
      key = "track",
      value = "bindInt",
      -id,-chr,-start,
      -end,-sign,-clus,
      -kclus,-yInj,-sil_width
    ) %>% 
  dplyr::mutate(
    track = stringr::str_replace(
        string = track,
        pattern = '^.*_(.*)GFP$',
        replacement = '\\1'
      ),
    track = base::factor(
        x = track,
        levels = base::c("Dichaete","Grainyhead","Eyeless"),
        ordered = TRUE
      )
    ) %>%
 dplyr::arrange(kclus,yInj,track)

rect <- clusDis %>%
  .GlobalEnv$rectAdd(
      df = .,
      gap = 100L,
      groups = groups_
    ) %>%
  dplyr::bind_cols(
      .,cols3[1:base::nrow(resK$centers)]
    ) %>%
  dplyr::mutate(
    clus = base::factor(
        x = clus,
        levels = base::seq(1,base::nrow(resK$centers),1),
        ordered = TRUE
      ),
    startX = stringr::str_replace(
        string = startX,
        pattern = '^.*_(.*)GFP$',
        replacement = '\\1'
      ),
    endX = str_replace(
        string = endX,
        pattern = '^.*_(.*)GFP$',
        replacement = '\\1'
      )
    )

rangE <- resViz %$%
  base::range(bindInt)
```

## [7.3.] Evaluate the data
```{r}
resViz %>%
 dplyr::arrange(kclus,sil_width) %>% 
  dplyr::group_by(kclus) %>% 
  dplyr::filter(
      dplyr::row_number() %in% base::c(1,n())
    )
```

## [7.4.] Save & load resViz
```{r}
base::saveRDS(
    object = resViz,
    file = base::paste0(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/"),
        base::format(base::Sys.time(), "%Y%m%d"),
        "_resViz_DichaeteOnly_zscores",
        "_clus", clusChos,
        "_FDR", FDR,
        "_algr", stringr::str_replace(algr, "-",""),
        "_seed", seed,
        ".rds"
      ),
    compress = TRUE
  )
```

```{r}
resViz <- base::readRDS(
    file = base::list.files(
        here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/")
      ) %>%
    stringr::str_subset('20190424_resViz_')
  )
```

## [7.5.] DataViz
```{r}
plot_heat <- ggplot2::ggplot() +
  geom_tile(
      data = resViz,
      mapping = aes(
          x = track,
          y = yInj,
          fill = bindInt
        ),
      alpha = 1
    ) +
  theme_bw() +
  theme(
      panel.border = element_blank(),
      panel.grid.major = element_blank(),
      axis.text.y = element_blank(),
      axis.line.x = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title = element_blank(),
      axis.text.x = element_text(
        angle = 90,
        vjust = 0.5,
        hjust = 1
      ),
      aspect.ratio = 2
    ) +
  scale_fill_gradient2(
      limits = base::c(rangE[1],rangE[2]),
      low = "blue",
      mid = "white",
      high = "red"
    ) +
  geom_rect(
      data = rect,
      mapping = aes(
          ymin = startY,
          ymax = endY
        ),
      xmin = 0.5,
      xmax = 3.5,
      fill = "transparent",
      color = "black"
    ) +
  geom_rect(
      data = rect,
      mapping = aes(
          ymin = startY,
          ymax = endY,
          fill = clus
        ),
      xmin = -0.15,
      xmax = 0.35,
      alpha = 1,
      color = "transparent",
      fill = cols3[1:nrow(resK$centers)]
    ) +
  geom_text(
      data = rect,
      mapping = aes(
          x = 0.1,
          y = base::round((endY-startY)/2)+startY,
          label = clus
        ),
      angle = 90,
      size = 3
    ) +
  scale_x_discrete(
      expand = ggplot2::expansion(
        add = base::c(1.25,0.6)
      )
    ) +
  scale_y_discrete(
      expand = ggplot2::expansion(
        add = base::c(80L,80L)
      )
    ) +
  guides(
      fill = guide_colourbar(
        label.position = "right",
        title.position = "left",
        title.theme = element_text(
            angle = 90,
            hjust = 0.5
          ),
        ticks=T,
        nbin=100,
        barheight=10,
        label=T,
        barwidth=0.5
      )
    )
base::print(plot_heat)
```

## [7.6.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
    ggplot2::ggsave(
      filename = base::paste0(
          here::here("results/20181205_NanoDam_DichaeteOgre_GrhEyD/"),
          base::format(base::Sys.time(), "%Y%m%d"),
          "_resKclus_heatmap_DichaeteOnly_zscores",
          "_clus", clusChos,
          "_FDR", FDR,
          "_algr", stringr::str_replace(algr, "-",""),
          "_seed", seed,
          ".", ext
        ),
      plot = plot_heat,
      device = ext,
      dpi = 300,
      width = 4,
      height = 8
    )
  }
```

##<<unnecessary_start>>

##---------------------##
##----tSNE_analysis----##
##---------------------##

## [5.23.] Prepare data for tSNE
```{r}
tmp <- resKclus %>%
 dplyr::arrange(kclus,sil_width) %>%
  dplyr::select(id, !!groups$profile) %>%
  distinct(
    DichaeteGal4_DichaeteGFP,
    DichaeteGal4_EyelessGFP,
    DichaeteGal4_GrainyheadGFP,
    OgreGal4_DichaeteGFP,
    OgreGal4_EyelessGFP,
    .keep_all = TRUE
  ) %>%
  tibble::column_to_rownames(.,var = "id")
```

## [5.24.] Run tSNE reduction with seed0
```{r}
set.seed(0)
res_tsne <-  Rtsne::Rtsne(
  X = tmp,
  dims = 2,
  perplexity = 30,
  verbose = TRUE,
  max_iter = 2000
)
```

## [5.25.] Prepare data for visualization
```{r}
model <- base::as.data.frame(res_tsne$Y) %>%
  cbind(
    .,
    resKclus %>%
     dplyr::arrange(kclus,sil_width) %>%
      dplyr::select(1,7)
  ) %>%
  dplyr::mutate(
    kclus = base::factor(
      kclus,
      levels = base::seq(1,base::nrow(resK$centers),1),
      ordered = TRUE
    )
  )
```

## [5.26.] Visualize tSNE
```{r}
plot_tsne <- ggplot2::ggplot(
    data = model,
    aes(
      x = V1,
      y = V2,
      colour = kclus
    )
  ) +
  geom_point(
    size = 0.25
  ) +
  scale_colour_manual(
    limits = base::seq(1,base::nrow(resK$centers),1),
    breaks = base::seq(1,base::nrow(resK$centers),1),
    labels = base::seq(1,base::nrow(resK$centers),1),
    values = cols3[1:nrow(resK$centers)],
    guide = guide_legend(
      label.position = "right",
      title.position = "left",
      direction = "vertical",
      title.theme = element_text(
        angle = 90,
        hjust = 0.5
      )
    )
  )
base::print(plot_tsne)
```

## [5.27.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
  ggplot2::ggsave(
    filename = base::paste0(
      here::here("results/20181205_NanoDam_DichaeteOgre_GrhEyD/20181207_resKclus_RtSNE_FDR25_seed0_iter2000_perpl30_dims2_V1_V2_k9_zscores."),
      ext
    ),
    plot = plot_tsne,
    device = ext,
    dpi = 300,
    width = 6,
    height = 5
  )
}
```

##<<unnecessary_end>>

##------------------------##
##----Cluster_analysis----##
##------------------------##

## [5.23.] Change format of tibble
```{r}
coln <- groups %>%
  dplyr::filter(
      stringr::str_detect(profile,"^Dichaete")
    ) %>% 
  dplyr::pull(profile) %>%
  base::append(base::c("id","kclus"),.)

lev <- base::c(
    "Dichaete","Grainyhead","Eyeless"
  )

tmp <- resKclus %>%
  dplyr::select(coln) %>%
  tidyr::gather(
      key = "track",
      value = "bind_int",
      -id,-kclus
    ) %>%
  dplyr::mutate(
    track = base::factor(
        x = track,
        levels = dplyr::pull(groups_,profile),
        ordered = TRUE
      ),
    kclus = base::factor(
      x = kclus,
      levels = base::seq(base::nrow(resK$centers),1, -1),
      ordered = TRUE
    ) 
  ) %>%
 dplyr::arrange(kclus,id,track)
```

## [5.24.] Plot mean intensities
```{r}
plot_stats <- ggplot2::ggplot(
      data = tmp,
      aes(
        x = track,
        y = 2^bind_int
      )
    ) +
  geom_boxplot(
      outlier.shape = NA
    ) +
  scale_y_continuous(
      position = "right",
      limits = base::c(0,3),
      breaks = base::c(0,1,2,3)
    ) +
  facet_grid(
      facets = kclus ~ .,
      switch = "y"
    ) +
  geom_hline(
      yintercept = 1,
      linetype = "dashed"
    ) +
  theme(
      axis.text.x = element_text(
          angle = 90,
          hjust = 1,
          vjust = 0.5
        ),
      axis.title.x = element_blank(),
      axis.title = element_blank(),
      aspect.ratio = 0.8,
      strip.placement = "outside"
    )
base::print(plot_stats)
```

## [5.25.] Add colours to strips according to cluster affiliation
```{r}
g <- ggplot2::ggplot_gtable(
    ggplot2::ggplot_build(plot_stats)
  )
strip_l <- base::which(
    base::grepl('strip-l', g$layout$name)
  )

k = 1L
for(i in strip_l){
    j <- base::which(
      base::grepl(
          pattern = 'rect',
          x = g$grobs[[i]]$grobs[[1]]$childrenOrder
        )
      )
    g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- base::rev(
        cols3[1:base::nrow(resK$centers)]
      )[k]
    k = k+1
    base::cat("k:\t", k,"\ti:\t",i,"\n")
  }
grid::grid.draw(g)
base::plot(g)
```

## [5.24.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
    ggplot2::ggsave(
      filename = base::paste0(
          here::here("results/20181205_NanoDam_DichaeteOgre_GrhEyD/"),
          base::format(base::Sys.time(), "%Y%m%d"),
          "_resKclus_boxplot_zscores",
          "_FDR", FDR,
          "_clus", clusChos,
          "_algr", stringr::str_replace(algr, "-",""),
          "_seed", seed,
          "_outlierNA",
          ".", ext
        ),
      plot = plot_stats,
      device = ext,
      dpi = 300,
      width = 2,
      height = 12
    )
  }
```

##<<unnecessary_start>>

## [5.25.] phes5-to-flox2 ratios
```{r}
clusK <- tibble::tibble(
    id = base::names(resK$cluster),
    kclus = resK$cluster
  )

resKclus <- res %>%
  dplyr::mutate(
    id = stringr::str_c(
      chr,start,end,sign,clus,
      sep = "_"
      )
  ) %>%
  merge(
    .,
    clusK,
    by = "id"
  )

resKclus <- resKclus %>%
  dplyr::mutate(
    fezf2 = log2(2^(flox2_fezf2)/2^(phes5_fezf2)),
    cux2 = log2(2^(flox2_cux2)/2^(phes5_cux2)),
    pou3f2 = log2(2^(flox2_pou3f2)/2^(phes5_pou3f2))
  ) %>%
  dplyr::select(1:6,13:16) %>%
  gather(
    key = "track",
    value = "bind_rat",
    -id,-chr,-start,-end,-sign,-clus,-kclus
  )
```

## [5.26.] Convert variables into base::factors for plotting
```{r}
id_levels <- resKclus %>%
  dplyr::select(id) %>%
  base::unlist() %>%
  base::unname()%>% 
  unique

resKclus <- resKclus %>%
  dplyr::mutate(
    id = base::factor(
      id,
      levels = id_levels,
      ordered = TRUE
    ),
    track = base::factor(
      track,
      levels = base::c("cux2","fezf2", "pou3f2"),
      ordered = TRUE
    )
  )
```

## [5.27.] Plot phes5-to-flox2 ratios
```{r}
plot_ratio <- ggplot2::ggplot(
    data = resKclus,
    aes(
      x = track,
      y = bind_rat
    )
  ) +
  geom_boxplot() +
  facet_wrap(
    ~kclus,
    nrow = 1
  ) +
  theme(
    axis.text.x = element_text(
      angle = 90,
      hjust = 1,
      vjust = 0.5
    )
  )
base::print(plot_ratio)
```

## [5.28.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
  ggplot2::ggsave(
    filename = base::paste0(
      here::here("results/20181012_phes5Flox2_cux2Fezf2Pou3f2_reproPeak/20181022_resKclus_ratios_FDR150."),
      ext
    ),
    plot = plot_ratio,
    device = ext,
    dpi = 300,
    width = 6,
    height = 4
  )
}
```

## [5.29.] Apply adegenet package to FDR25 data 
##### Note: __Deprecated__
```{r}
tmp <- resKclus %>%
 dplyr::arrange(kclus,sil_width) %>%
  dplyr::select(id, !!groups$profile) %>%
  distinct(
    DichaeteGal4_DichaeteGFP,
    DichaeteGal4_EyelessGFP,
    DichaeteGal4_GrainyheadGFP,
    OgreGal4_DichaeteGFP,
    OgreGal4_EyelessGFP,
    .keep_all = TRUE
  ) %>%
  tibble::column_to_rownames(.,var = "id")

set.seed(0)
adeK <- adegenet::find.clusters(
  x = tmp,
  max.n.clust = 40,
  n.pca = 3,
  choose.n.clust = FALSE,
  criterion = "diffNgroup",
  stat = "BIC",
  n.iter=2000
)
adeK$stat

adeDAPC <- adegenet::dapc(
  x = tmp,
  grp = adeK$grp
)
ade4::scatter(adeDAPC)
```

##----------------------##
##----PAM_clustering----##
##----------------------##

## [6.0.] Prepare data for PAM analysis
```{r}
tmp <- resKclus %>%
 dplyr::arrange(kclus,sil_width) %>%
  dplyr::select(id, !!groups$profile) %>%
  distinct(
    DichaeteGal4_DichaeteGFP,
    DichaeteGal4_EyelessGFP,
    DichaeteGal4_GrainyheadGFP,
    OgreGal4_DichaeteGFP,
    OgreGal4_EyelessGFP,
    .keep_all = TRUE
  ) %>%
  tibble::column_to_rownames(.,var = "id")
```

## [6.1.] Partitioning around medoids - PAM
```{r}
set.seed(0)

pam <- cluster::pam(
    x = tmp,
    k = 9
  )
```

## [6.2.] Validation via silhouette plots
```{r}
sil <- cluster::silhouette(
    x = pam$clustering,
    dist = dist(tmp)
  )

factoextra::fviz_silhouette(sil)
```

## [6.3.] Include cluster assignments
```{r}
res_pam <- tibble::tibble(
    id = base::names(pam$clustering),
    pamclus = pam$clustering
  ) %>%
  base::merge(
    x = .,
    y = resKclus %>%
     dplyr::arrange(kclus,sil_width),
    by = "id"
  )
```

## [6.4.] Save res_pam
```{r}
base::saveRDS(
  object = res_pam,
  file = here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/20181206_res_pam_FDR25_seed0_k9.rds"),
  compress = TRUE
)
```

## [6.5.] PAM via fpc package
```{r}
set.seed(0)

res_pamk <- fpc::pamk(
    data = resClus,
    krange = 3:7,
    criterion = "asw"
  )

sil <- cluster::silhouette(
    x = res_pamk$pamobject$clustering,
    dist = dist(resClus)
  )

factoextra::fviz_silhouette(sil)
```

## [6.6.] Prepare data for tSNE
```{r}
tmp <- res_pam %>%
 dplyr::arrange(pamclus,sil_width) %>%
  dplyr::select(id, !!groups$profile) %>%
  distinct(
    DichaeteGal4_DichaeteGFP,
    DichaeteGal4_EyelessGFP,
    DichaeteGal4_GrainyheadGFP,
    OgreGal4_DichaeteGFP,
    OgreGal4_EyelessGFP,
    .keep_all = TRUE
  ) %>%
  tibble::column_to_rownames(.,var = "id")
```

## [6.7.] Run tSNE reduction with seed0
```{r}
set.seed(0)
res_tsne <-  Rtsne::Rtsne(
  X = tmp,
  dims = 2,
  perplexity = 30,
  verbose = TRUE,
  max_iter = 2000
)
```

## [6.8.] Prepare data for visualization
```{r}
model <- base::as.data.frame(res_tsne$Y) %>%
  cbind(
    .,
    res_pam %>%
     dplyr::arrange(pamclus,sil_width) %>%
      dplyr::select(1,2)
  ) %>%
  dplyr::mutate(
    pamclus = base::factor(
      pamclus,
      levels = base::seq(1,max(unique(res_pam$pamclus)),1),
      ordered = TRUE
    )
  )
```

## [6.9.] Visualize tSNE
```{r}
plot_tsne <- ggplot2::ggplot(
    data = model,
    aes(
      x = V1,
      y = V2,
      colour = pamclus
    )
  ) +
  geom_point(
    size = 0.25
  ) +
  scale_colour_manual(
    limits = base::seq(1,max(unique(res_pam$pamclus)),1),
    breaks = base::seq(1,max(unique(res_pam$pamclus)),1),
    labels = base::seq(1,max(unique(res_pam$pamclus)),1),
    values = cols3[1:max(unique(res_pam$pamclus))],
    guide = guide_legend(
      label.position = "right",
      title.position = "left",
      direction = "vertical",
      title.theme = element_text(
        angle = 90,
        hjust = 0.5
      )
    )
  )
base::print(plot_tsne)
```

## [6.10.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
  ggplot2::ggsave(
    filename = base::paste0(
      here::here("results/20181205_NanoDam_DichaeteOgre_GrhEyD/20181206_res_pam_RtSNE_FDR25_seed0_iter2000_perpl30_dims2_V1_V2_k9."),
      ext
    ),
    plot = plot_tsne,
    device = ext,
    dpi = 300,
    width = 6,
    height = 5
  )
}
```

## [6.11.] Prepare for visualization
##### Note: generate 'idLevels' vector by 'tmp %>% dplyr::group_by(id) %>% distinct(id) %>% base::unlist() %>% base::unname()'
```{r}
tmp <- res_pam %>%
  base::as.tibble %>% 
  dplyr::mutate(
    pamclus = base::factor(
      pamclus,
      levels = base::seq(1,max(unique(res_pam$pamclus))),
      ordered = TRUE
    )
  ) %>%
 dplyr::arrange(pamclus,sil_width)

clusDis <- res_pam %>%
  dplyr::group_by(pamclus) %>%
  dplyr::summarise(amount = dplyr::n()) %>% 
  dplyr::rename(., clus=pamclus)

resViz <- tmp %>%
  dplyr::mutate(
    yInj = seqAdd(clusDis, gap=100L)
  ) %>%
  gather(
    key = "track",
    value = "bindInt",
    -id,-chr,-start,-end,-sign,-clus,-kclus,-yInj,-sil_width,-pamclus
  ) %>% 
  dplyr::mutate(
    track = base::factor(
      track,
      levels = groups$profile,
      ordered = TRUE
    )
  ) %>%
 dplyr::arrange(pamclus,yInj,track)

rect <- rectAdd(clusDis, gap=100L) %>%
  cbind(.,cols3[1:max(unique(res_pam$pamclus))]) %>%
  dplyr::mutate(
    clus = base::factor(
      clus,
      levels = base::seq(1,max(unique(res_pam$pamclus)),1),
      ordered = TRUE
    )
  )

rangE <- resViz %$%
  range(bindInt)
```

## [6.12.] Evaluation of resViz
```{r}
resViz %>%
 dplyr::arrange(pamclus,sil_width) %>% 
  dplyr::group_by(pamclus) %>% 
  dplyr::filter(row_number() %in% base::c(1,n()))
```

## [6.13.] Save resViz
```{r}
base::saveRDS(
  object = resViz,
  file = here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/20181206_resViz_of_res_pam_FDR25_seed0_k9.rds"),
  compress = TRUE
)
```

## [6.14.] DataViz
```{r}
plot_heat <- ggplot2::ggplot() +
  geom_tile(
     data = resViz,
    aes(
      x = track,
      y = yInj,
      fill = bindInt
    ),
    alpha = 1
  ) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title = element_blank(),
    axis.text.x = element_text(
      angle = 90,
      vjust = 0.5,
      hjust = 1
    ),
    aspect.ratio = 2
  ) +
  scale_fill_gradient2(
    limits = base::c(rangE[1],rangE[2]),
    low = "darkblue",
    mid = "white",
    high = "darkred"
  ) +
  geom_rect(
    data = rect,
    aes(
      ymin = rect$startY,
      ymax = rect$endY
    ),
    xmin = 0.5,
    xmax = 5.5,
    fill = "transparent",
    color = "black"
  ) +
  geom_rect(
    data = rect,
    aes(
      ymin = rect$startY,
      ymax = rect$endY,
      fill = rect$clus
    ),
    xmin = -0.15,
    xmax = 0.35,
    alpha = 0.3,
    color = "transparent",
    fill = cols3[1:max(unique(res_pam$pamclus))]
  ) +
  geom_text(
    data = rect,
    aes(
      x = 0.1,
      y = base::round((rect$endY-rect$startY)/2)+rect$startY,
      label = rect$clus
    ),
    angle = 90,
    size = 3
  ) +
  scale_x_discrete(
    expand = expand_scale(
      add=c(1.25,0.6)
    )
  ) +
  scale_y_discrete(
    expand = expand_scale(
      add = base::c(80L,80L)
    )
  ) +
  guides(
    fill = guide_colourbar(
      label.position = "right",
      title.position = "left",
      title.theme = element_text(
        angle = 90,
        hjust = 0.5
      ),
      ticks=T,
      nbin=100,
      barheight=10,
      label=T,
      barwidth=0.5
    )
  )
base::print(plot_heat)
```

## [6.15.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
  ggplot2::ggsave(
    filename = base::paste0(
      here::here("results/20181205_NanoDam_DichaeteOgre_GrhEyD/20181206_res_pam_heatmap_FDR25_seed0_k9."),
      ext
    ),
    plot = plot_heat,
    device = ext,
    dpi = 300,
    width = 4,
    height = 8
  )
}
```

##-------------------------##
##----BIC_EM_clustering----##
##-------------------------##

## [8.0.] Prepare data for BIC_EM
```{r}
tmp <- resKclus %>%
 dplyr::arrange(kclus,sil_width) %>%
  dplyr::select(id, !!groups$profile) %>%
  distinct(
    DichaeteGal4_DichaeteGFP,
    DichaeteGal4_EyelessGFP,
    DichaeteGal4_GrainyheadGFP,
    OgreGal4_DichaeteGFP,
    OgreGal4_EyelessGFP,
    .keep_all = TRUE
  ) %>%
  tibble::column_to_rownames(.,var = "id")
```

## [8.1.] Cluster data
```{r}
set.seed(0)
fit <- mclust::Mclust(
    data = tmp,
    G=1:10
  )

summary(fit)
fit$BIC
plot(fit, what="BIC")
```

## [8.2.] Mclust package functions
```{r}
set.seed(0)
mclust::clPairs(tmp)

##Initialized by hierachical clustering
BIC <- mclust::mclustBIC(
    data = tmp,
    G = 1:10
  )

##Based on Integrated Complete-data Likelihood
mclust::mclustICL(
    data = tmp,
    G = 1:10
  )

##Bootstrap sequential LRT
mclust::mclustBootstrapLRT(
  data = tmp,
  maxG = 10,
  modelName = "VVV"
)

##Dimension reduction
bic <- mclust::Mclust(
    data = tmp,
    x = BIC
  )
bicdr <- mclust::MclustDR(
  object = bic
  )
plot(bicdr, what = "boundaries", ngrid = 200L)
```

## [8.3.] Generate cluster distribution table
```{r}
clusDis <- fitClus %>%
  dplyr::group_by(Mclus) %>%
  dplyr::summarise(amount = dplyr::n()) %>% 
  dplyr::rename(., clus=Mclus)
```

## [8.4.] Validation via silhouette plots
```{r}
sil <- cluster::silhouette(
    x = fit$classification,
    dist = dist(tmp)
  )

factoextra::fviz_silhouette(sil)
```

## [8.5.] Generate cluster lookup table
```{r}
res_mclus <- tibble::tibble(
    id = base::names(fit$classification),
    Mclus = fit$classification
  ) %>%
  base::merge(
    x = .,
    y = resKclus %>%
     dplyr::arrange(kclus,sil_width),
    by = "id"
  )
```

## [8.6.] Save res_mclus
```{r}
base::saveRDS(
  object = res_mclus,
  file = here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/20181206_res_mclus_FDR25_seed0_k9.rds"),
  compress = TRUE
)
```

## [8.7.] Prepare data for tSNE
```{r}
tmp <- res_mclus %>%
 dplyr::arrange(Mclus,sil_width) %>%
  dplyr::select(id, !!groups$profile) %>%
  distinct(
    DichaeteGal4_DichaeteGFP,
    DichaeteGal4_EyelessGFP,
    DichaeteGal4_GrainyheadGFP,
    OgreGal4_DichaeteGFP,
    OgreGal4_EyelessGFP,
    .keep_all = TRUE
  ) %>%
  tibble::column_to_rownames(.,var = "id")
```

## [8.8.] Run tSNE reduction with seed0
```{r}
set.seed(0)
res_tsne <-  Rtsne::Rtsne(
  X = tmp,
  dims = 2,
  perplexity = 30,
  verbose = TRUE,
  max_iter = 2000
)
```

## [8.9.] Prepare data for visualization
```{r}
model <- base::as.data.frame(res_tsne$Y) %>%
  cbind(
    .,
    res_mclus %>%
     dplyr::arrange(Mclus,sil_width) %>%
      dplyr::select(1,2)
  ) %>%
  dplyr::mutate(
    Mclus = base::factor(
      Mclus,
      levels = base::seq(1,max(unique(res_mclus$Mclus)),1),
      ordered = TRUE
    )
  )
```

## [8.10.] Visualize tSNE
```{r}
plot_tsne <- ggplot2::ggplot(
    data = model,
    aes(
      x = V1,
      y = V2,
      colour = Mclus
    )
  ) +
  geom_point(
    size = 0.25
  ) +
  scale_colour_manual(
    limits = base::seq(1,max(unique(res_mclus$Mclus)),1),
    breaks = base::seq(1,max(unique(res_mclus$Mclus)),1),
    labels = base::seq(1,max(unique(res_mclus$Mclus)),1),
    values = cols3[1:max(unique(res_mclus$Mclus))],
    guide = guide_legend(
      label.position = "right",
      title.position = "left",
      direction = "vertical",
      title.theme = element_text(
        angle = 90,
        hjust = 0.5
      )
    )
  )
base::print(plot_tsne)
```

## [8.11.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
  ggplot2::ggsave(
    filename = base::paste0(
      here::here("results/20181205_NanoDam_DichaeteOgre_GrhEyD/20181206_res_mclus_RtSNE_FDR25_seed0_iter2000_perpl30_dims2_V1_V2_k10."),
      ext
    ),
    plot = plot_tsne,
    device = ext,
    dpi = 300,
    width = 6,
    height = 5
  )
}
```

## [8.12.] Prepare for visualization
##### Note: generate 'idLevels' vector by 'tmp %>% dplyr::group_by(id) %>% distinct(id) %>% base::unlist() %>% base::unname()'
```{r}
tmp <- res_mclus %>%
  base::as.tibble %>% 
  dplyr::mutate(
    Mclus = base::factor(
      Mclus,
      levels = base::seq(1,max(unique(res_mclus$Mclus))),
      ordered = TRUE
    )
  ) %>%
 dplyr::arrange(Mclus,sil_width)

clusDis <- res_mclus %>%
  dplyr::group_by(Mclus) %>%
  dplyr::summarise(amount = dplyr::n()) %>% 
  dplyr::rename(., clus=Mclus)

resViz <- tmp %>%
  dplyr::mutate(
    yInj = seqAdd(clusDis, gap=100L)
  ) %>%
  gather(
    key = "track",
    value = "bindInt",
    -id,-chr,-start,-end,-sign,-clus,-kclus,-yInj,-sil_width,-Mclus
  ) %>% 
  dplyr::mutate(
    track = base::factor(
      track,
      levels = groups$profile,
      ordered = TRUE
    )
  ) %>%
 dplyr::arrange(Mclus,yInj,track)

rect <- rectAdd(clusDis, gap=100L) %>%
  cbind(.,cols3[1:max(unique(res_mclus$Mclus))]) %>%
  dplyr::mutate(
    clus = base::factor(
      clus,
      levels = base::seq(1,max(unique(res_mclus$Mclus)),1),
      ordered = TRUE
    )
  )

rangE <- resViz %$%
  range(bindInt)
```

## [8.13.] Evaluation of resViz
```{r}
resViz %>%
 dplyr::arrange(Mclus,sil_width) %>% 
  dplyr::group_by(Mclus) %>% 
  dplyr::filter(row_number() %in% base::c(1,n()))
```

## [8.14.] Save resViz
```{r}
base::saveRDS(
  object = resViz,
  file = here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/20181206_resViz_of_res_mclus_FDR25_seed0_k9.rds"),
  compress = TRUE
)
```

## [8.15.] DataViz
```{r}
plot_heat <- ggplot2::ggplot() +
  geom_tile(
     data = resViz,
    aes(
      x = track,
      y = yInj,
      fill = bindInt
    ),
    alpha = 1
  ) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title = element_blank(),
    axis.text.x = element_text(
      angle = 90,
      vjust = 0.5,
      hjust = 1
    ),
    aspect.ratio = 2
  ) +
  scale_fill_gradient2(
    limits = base::c(rangE[1],rangE[2]),
    low = "darkblue",
    mid = "white",
    high = "darkred"
  ) +
  geom_rect(
    data = rect,
    aes(
      ymin = rect$startY,
      ymax = rect$endY
    ),
    xmin = 0.5,
    xmax = 5.5,
    fill = "transparent",
    color = "black"
  ) +
  geom_rect(
    data = rect,
    aes(
      ymin = rect$startY,
      ymax = rect$endY,
      fill = rect$clus
    ),
    xmin = -0.15,
    xmax = 0.35,
    alpha = 0.3,
    color = "transparent",
    fill = cols3[1:max(unique(res_mclus$Mclus))]
  ) +
  geom_text(
    data = rect,
    aes(
      x = 0.1,
      y = base::round((rect$endY-rect$startY)/2)+rect$startY,
      label = rect$clus
    ),
    angle = 90,
    size = 3
  ) +
  scale_x_discrete(
    expand = expand_scale(
      add=c(1.25,0.6)
    )
  ) +
  scale_y_discrete(
    expand = expand_scale(
      add = base::c(80L,80L)
    )
  ) +
  guides(
    fill = guide_colourbar(
      label.position = "right",
      title.position = "left",
      title.theme = element_text(
        angle = 90,
        hjust = 0.5
      ),
      ticks=T,
      nbin=100,
      barheight=10,
      label=T,
      barwidth=0.5
    )
  )
base::print(plot_heat)
```

## [8.16.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
  ggplot2::ggsave(
    filename = base::paste0(
      here::here("results/20181205_NanoDam_DichaeteOgre_GrhEyD/20181206_res_mclus_heatmap_FDR25_seed0_k10."),
      ext
    ),
    plot = plot_heat,
    device = ext,
    dpi = 300,
    width = 4,
    height = 8
  )
}
```

##--------------------##
##----PCA_analysis----##
##--------------------##

## [8.8.] PCA analysis
##### Note: 'factoextra::fviz_pca_ind(pca,label = "none",habillage = res_mclus$Mclus)'
```{r}
pca <- stats::prcomp(
    x = resKclus %>%
      dplyr::select(8:11)
  )

pca_sum <- factoextra::facto_summarize(
    X = pca,
    element = "ind",
    axes = base::c(1,2,3,4),
    result =  base::c("coord", "contrib", "cos2")
  )

pca_contr <- factoextra::facto_summarize(
    X = pca,
    element = "var",
    axes = base::c(1,2,3,4),
    result =  base::c("coord", "contrib", "cos2")
  )

res_pca <- cbind(resKclus,pca_sum)
```

## [8.9.] Generate additional variables
```{r}
res_pca <- res_pca %>%
  dplyr::mutate(
    phes5_flox2 = log2((2^phes5_cux2+2^phes5_fezf2)/(2^flox2_cux2+2^flox2_fezf2)),
    cux2_fezf2 = log2((2^phes5_cux2+2^flox2_cux2)/(2^phes5_fezf2+2^flox2_fezf2)),
    kclus = base::factor(
      kclus,
      levels = base::seq(1,base::nrow(resK$centers),1),
      ordered = TRUE
    )
  )
```

## [8.10.] Determine contribution parameter
```{r}
end <- pca_contr %>%
  remove_rownames() %>% 
  dplyr::select(1:5) %>% 
  gather(
    key = "param",
    value = "value",
    -name
  )

 start <- end %>%
  dplyr::mutate(
    value = 0
  )%>%
  tidyr::spread(
    key = "param",
    value = "value"
  )
 
coord <- pca_contr %>%
  remove_rownames() %>% 
  dplyr::select(1:5) %>% 
  gather(
    key = "param",
    value = "value",
    -name
  ) %>%
  dplyr::mutate(
    value = value*4
  ) %>%
  tidyr::spread(
    key = "param",
    value = "value"
  ) %>% 
  rbind(., start) %>%
 dplyr::arrange(name,abs(Dim.1))
```

## [8.11.] Plot phes5_flox2
```{r}
plot_pca <- ggplot2::ggplot() +
  geom_point(
    data = res_pca,
    aes(
      x=Dim.1,
      y=Dim.2,
      fill = phes5_flox2
    ),
    alpha=0.6,
    colour="black",
    pch = 21,
    stroke = 0.1
  ) +
  geom_hline(
    yintercept = 0,
    linetype = "dashed"
  ) +
  geom_vline(
    xintercept = 0,
    linetype = "dashed"
  ) +
  scale_fill_gradient2(
    limits = base::c(-8,8),
    low = "darkblue",
    mid = "white",
    high = "darkred"
  ) +
  geom_line(
    data = coord %>%
      dplyr::filter(grepl('flox2',name)),
    aes(
      x=Dim.1,
      y=Dim.2,
      group = name
    ),
    arrow = arrow(
      length=unit(0.30,"cm"),
      ends="last",
      type = "closed",
      angle = 15
      ),
    linetype = "dashed"
  ) +
  geom_text(
    data = coord %>%
      dplyr::filter(
        grepl('flox2',name) &
        Dim.1 != 0L
      ),
    aes(
      x = Dim.1,
      y = Dim.2,
      label = name
    )
  ) +
  geom_line(
    data = coord %>%
      dplyr::filter(grepl('phes5',name)),
    aes(
      x=Dim.1,
      y=Dim.2,
      group = name
    ),
    arrow = arrow(
      length=unit(0.30,"cm"),
      ends="first",
      type = "closed",
      angle = 15
      ),
    linetype = "dashed"
  )  +
  geom_text(
    data = coord %>%
      dplyr::filter(
        grepl('phes5',name) &
        Dim.1 != 0L
      ),
    aes(
      x = Dim.1,
      y = Dim.2,
      label = name
    )
  ) +
  guides(
    fill = guide_colourbar(
      label.position = "right",
      title.position = "left",
      title.theme = element_text(
        angle = 90,
        hjust = 0.5
      ),
      ticks=T,
      nbin=100,
      barheight=10,
      label=T,
      barwidth=0.5
    )
  )
  xlim(-4,4)
base::print(plot_pca)
```

## [8.7.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
  ggplot2::ggsave(
    filename = base::paste0(
      here::here("results/20181119_phes5Flox2_cux2Fezf2_tracks/20181123_pca_phes5Flox2_cux2Fezf2_FDR25_phes5_vs_flox2_v3_seed0."),
      ext
    ),
    plot = plot_pca,
    device = ext,
    dpi = 300,
    width = 6,
    height = 4
  )
}
```

## [8.11.] Plot phes5_flox2
```{r}
plot_pca <- ggplot2::ggplot() +
  geom_point(
    data = res_pca,
    aes(
      x=Dim.1,
      y=Dim.3,
      fill = cux2_fezf2
    ),
    alpha=0.6,
    colour="black",
    pch = 21,
    stroke = 0.1
  ) +
  geom_hline(
    yintercept = 0,
    linetype = "dashed"
  ) +
  geom_vline(
    xintercept = 0,
    linetype = "dashed"
  ) +
  scale_fill_gradient2(
    limits = base::c(-8,8),
    low = "darkblue",
    mid = "white",
    high = "darkred"
  ) +
  geom_line(
    data = coord %>%
      dplyr::filter(grepl('flox2',name)),
    aes(
      x=Dim.1,
      y=Dim.3,
      group = name
    ),
    arrow = arrow(
      length=unit(0.30,"cm"),
      ends="last",
      type = "closed",
      angle = 15
      ),
    linetype = "dashed"
  ) +
  geom_text(
    data = coord %>%
      dplyr::filter(
        grepl('flox2',name) &
        Dim.1 != 0L
      ),
    aes(
      x = Dim.1,
      y = Dim.3,
      label = name
    )
  ) +
  geom_line(
    data = coord %>%
      dplyr::filter(grepl('phes5',name)),
    aes(
      x=Dim.1,
      y=Dim.3,
      group = name
    ),
    arrow = arrow(
      length=unit(0.30,"cm"),
      ends="first",
      type = "closed",
      angle = 15
      ),
    linetype = "dashed"
  )  +
  geom_text(
    data = coord %>%
      dplyr::filter(
        grepl('phes5',name) &
        Dim.1 != 0L
      ),
    aes(
      x = Dim.1,
      y = Dim.3,
      label = name
    )
  ) +
  guides(
    fill = guide_colourbar(
      label.position = "right",
      title.position = "left",
      title.theme = element_text(
        angle = 90,
        hjust = 0.5
      ),
      ticks=T,
      nbin=100,
      barheight=10,
      label=T,
      barwidth=0.5
    )
  ) +
  xlim(-4,4) +
  ylim(-4,4)
base::print(plot_pca)
```

## [8.7.] Save plot
```{r}
for(ext in base::c("pdf", "png")){
  ggplot2::ggsave(
    filename = base::paste0(
      here::here("results/20181119_phes5Flox2_cux2Fezf2_tracks/20181123_pca_phes5Flox2_cux2Fezf2_FDR25_phes5_vs_flox2_v3_seed0_Dim1Dim3."),
      ext
    ),
    plot = plot_pca,
    device = ext,
    dpi = 300,
    width = 6,
    height = 4
  )
}
```

##----------------------------##
##----Retrieve_coordinates----##
##----------------------------##

## [7.0.] Load res
##### Note: Previous dir: "data/20181012_phes5Flox2_cux2Fezf2Pou3f2_tracks/20181030_resKclus_FDR150.rds"
```{r}
resKclus <- base::readRDS(
  file = here::here("data/20181119_phes5Flox2_cux2Fezf2_tracks/20181123_resKclus_FDR25_seed0.rds")
)
```

## [7.1.] LiftOver coordinates to mm9
```{r}
mm10Tomm9.chain <- rtracklayer::import.chain(
    con = "/Users/robertkrautz/Documents/resources/mm10ToMm9.over.chain"
  )
(
  resKclus %>%
    dplyr::select(2:4) %>%
    dplyr::mutate(
      chr = stringr::str_c("chr",chr)
    ) %>% 
    GenomicRanges::makeGRangesFromDataFrame(.) %>%
    rtracklayer::liftOver(
      x = .,
      chain = mm10Tomm9.chain
    ) %>%
    base::as.tibble %>%
    dplyr::rename(.,chr=seqnames) %>% 
    dplyr::select(chr,start,end)
)
```

## [7.1.] Helper function to write peak sequences for every cluster
```{r}
coordinator <- function(k, tib, outdir, genome="mm10", fdr=150L){
  
  if(genome=="mm9"){
    mm10Tomm9.chain <- rtracklayer::import.chain(
      con = "/Users/robertkrautz/Documents/resources/mm10ToMm9.over.chain"
    )
  }
  
  tmpTib <- tib %>%
    dplyr::filter(
      kclus == k
    ) %>%
    dplyr::select(2:4) %>%
    when(
      genome == "mm10" ~
        dplyr::arrange(., chr,start),
      TRUE ~ 
        dplyr::mutate(
            .,
            chr = stringr::str_c("chr",chr)
          ) %>%
        GenomicRanges::makeGRangesFromDataFrame(.) %>%
        rtracklayer::liftOver(
            x = .,
            chain = mm10Tomm9.chain
          ) %>%
        base::as.tibble %>%
        dplyr::rename(.,chr=seqnames) %>%
        dplyr::arrange(chr,start) %>% 
        dplyr::select(chr,start,end)
    )
  
  fn <- here::here(
   base::paste0(
      outdir,
      base::format(base::Sys.time(), "%Y%m%d"),
      "_resKclus_FDR",
      fdr, "_",
      genome, "_",
      "kclus", k,
      ".bed"
    )
  )
  
  write.table(
    x = tmpTib,
    file = fn,
    quote = FALSE,
    sep = "\t",
    eol = "\n",
    row.names = FALSE,
    col.names = FALSE
  )
  return(fn)
}
```

## [7.2.] Apply writer() to all clusKs
```{r}
clusFiles <- purrr::map_chr(
  .x = resKclus %>%
    distinct(kclus) %>%
    base::unlist() %>%
    base::unname(),
  .f = coordinator,
  tib = resKclus,
  outdir = "data/20181119_phes5Flox2_cux2Fezf2_tracks/",
  genome = "mm9",
  fdr = 25L
)
clusFiles
```

##--------------------------##
##----Retrieve_sequences----##
##--------------------------##

## [6.0.] Load res
##### Note: see '[5.19.]'
```{r}
resKclus <- base::readRDS(
    file = here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/20181207_resKclus_FDR25_seed0_k9_zscores.rds")
  )
```

## [6.1.] Retrieve peak sequences
##### Note: Sequences derived from 'BSgenome.Mmusculus.UCSC.mm10'
```{r}
resSeq <- resKclus %>%
   dplyr::mutate(
    names = stringr::str_c("chr",chr),
    seq = pmap(
    base::list(
      names,
      start,
      end
    ),
    getSeq,
    x=Dmelanogaster
    )
  )
```

## [6.2.] Save peak sequences
```{r}
base::saveRDS(
  object = resSeq,
  file = here::here("data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/20181213_resSeq_FDR25_seed0_zscores.rds"),
  compress = TRUE
)
```

## [6.3.] Load peak sequences
```{r}
resSeq <- base::readRDS(
    file = here::here("data/20181126_phes5Flox2_cux2Fezf2_motifEnrichment/20181126_resSeq_FDR25_seed0.rds")
  )
```

## [6.4.1.] Convert resSeq into DNAStringSet
```{r}
resStr <- resSeq %>%
  dplyr::select(seq) %>%
  base::unlist() %>%
  base::unname()%>%
  Biostrings::DNAStringSet(.)
```

## [6.4.2.] Convert all sequences in resSeq to strings
```{r}
resSeq %>%
  sample_n(20) %>%
  dplyr::mutate(
    seqStr = purrr::map_chr(
      seq,
      toString
    )
  )
```

## [6.5.] Helper function to write peak sequences for every cluster
```{r}
writer <- function(k, tib, outdir, fdr = 25L){
  
  tmpTib <- tib %>%
    dplyr::filter(
      kclus == k
    ) %>%
    dplyr::mutate(
      id = stringr::str_c(">",chr,"_",start,"_",end),
      #id = stringr::str_c(">",id),
      seqStr = purrr::map_chr(
        seq,
        toString
      )
    ) %>%
    dplyr::select(id,seqStr)
  
  fn <- here::here(
   base::paste0(
      outdir,
      base::format(base::Sys.time(), "%Y%m%d"),
      "_resSeq_FDR",
      fdr, "_",
      "kclus", k,
      ".fa"
    )
  )
  
  write.table(
    x = tmpTib,
    file = fn,
    quote = FALSE,
    sep = "\n",
    eol = "\n",
    row.names = FALSE,
    col.names = FALSE
  )
  return(fn)
}
```

## [6.6.] Apply writer() to all clusKs
```{r}
clusFiles <- purrr::map_chr(
  .x = resKclus %>%
    distinct(kclus) %>%
    base::unlist() %>%
    base::unname(),
  .f = writer,
  tib = resSeq,
  outdir = "data/20180515_NanoDam_DichaeteOgre_GrhEyD_tracks/",
  fdr = 25L
)
```

##<<unnecessary_end>>
