---
title: "signal_enrichment"
author: "R_Krautz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## [0.0.] Load necessary packages
```{r message=FALSE}
base::library(tidyverse)
base::library(magrittr)
base::library(here)
base::library(RColorBrewer)
base::library(preprocessCore)

base::library(foreach)
base::library(doParallel)
doParallel::registerDoParallel(
    cores = 20
  )
```

## [0.1.] Prerequisites
```{r}
sel_chrom = base::c("2L","2R","3L","3R","4","X","Y")
```

## [0.2.] Helper function
```{r}
str_ignore <- function(vec,pattern){
  return(
      vec[!stringr::str_detect(vec,pattern)]
    )
  }
```

##-----------------##
##----Functions----##
##-----------------##

## [1.0.] filer() function to identify files of interest
```{r}
filer <- function(fdr, dir, ext='mergePeak'){
    return(
      base::list.files(
          path = dir,
          full.names = TRUE
        ) %>%
      stringr::str_subset(ext) %>%
      stringr::str_subset(
        base::paste0(".*/",fdr,'\\..*')
      )
    )
  }
```

## [1.1.] reader() function
```{r}
reader <- function(filename, fdr = 5L, chroms = sel_chrom, skip=1L){
  return(
    readr::read_delim(
        file = filename,
        delim = "\t",
        quote = "",
        col_names = base::c(
            "chr","start","end",
            "sign","score","strand",
            "thickStart","thickEnd","RGB"
          ),
        col_types = readr::cols_only(
            chr = readr::col_character(),
            start = readr::col_integer(),
            end = readr::col_integer(),
            sign = readr::col_double()
          ),
        skip = skip
      ) %>%
    dplyr::filter(
        chr %in% sel_chrom
      ) %>% 
    dplyr::mutate(
      cond = stringr::str_replace(
          string = filename,
          pattern = '.*/(.*)_peaks/.*',
          replacement = '\\1'
        )
      )
    )
  }
```

## [1.2.] merger() function to reduce peaks bedr-dependent
```{r}
merger <- function(df, chosenEngine="bedtools"){
    
    out <- tryCatch(
        {
          if(!bedr::check.binary(chosenEngine)){
            stop(
              base::paste0("Chosen engine:\t",chosenEngine,"\tnot available.\n")
            )
          }else{
            
            is.df.valid <- df %>%
              base::as.data.frame() %>%
              bedr::is.valid.region(
                  check.chr = FALSE
                )
            
            dfVal <- df %>%
              dplyr::filter(
                  dplyr::row_number() == base::which(is.df.valid)
                ) %>% 
              base::as.data.frame()
            
            dfSort <- bedr::bedr(
                engine = chosenEngine,
                input = base::list(i=dfVal),
                method = "sort",
                params = "",
                check.chr = FALSE,
                check.valid = TRUE,
                check.sort = FALSE
              )
            
            dfMerg <- bedr::bedr(
                engine = chosenEngine,
                input = base::list(i=dfSort),
                method = "merge",
                params = "-c 4 -o distinct",
                check.chr = FALSE,
                check.valid = TRUE,
                check.sort = TRUE,
                check.merge = FALSE
              )
            
            dfMerg %>%
              tibble::as.tibble() %>%
              dplyr::arrange(chr, start)
            
          }
      },
      error = function(cond){
          base::message(cond)
          return(NA)
        },
      warning = function(cond){
          base::message(cond)
          return(NA)
        }
    )
    
    return(out)
  }
```

## [1.3.] Helper function extract_matrix()
```{r}
extract_matrix <- function(track, regions, size) {
  sum <- base::suppressWarnings(
      .Call(
        "BWGFile_summary",
        base::path.expand(rtracklayer::path(track)), 
        base::as.character(GenomicRanges::seqnames(regions)),
        IRanges::ranges(regions),
        S4Vectors::recycleIntegerArg(
            size, "size", base::length(regions)
          ),
        "mean",
        base::as.numeric(NA_real_), 
        PACKAGE = "rtracklayer"
      )
    )
  return(
      base::do.call(rbind, sum)
    )
  }
```

##---------------##
##----Windows----##
##---------------##

## [2.0.] Apply filer() & reader()
#### files: "Cph_NanoDam_peaks_FDR5.mergePeak"; "Cph_TaDa_peaks_FDR5.mergePeak"
```{r}
FDR = 5L

fns <- purrr::map_chr(
    .x = base::c(
        here::here("data/")
      ),
    .f = .GlobalEnv$filer,
    fdr = FDR
  )

preSub <- purrr::map_dfr(
    .x = fns,
    .f = .GlobalEnv$reader,
    fdr = FDR
  )
```

## [2.1.] Evaluate
```{r}
preSub %>%
  dplyr::group_by(cond) %>%
  dplyr::summarise(n = dplyr::n())

preSub %>%
  dplyr::filter(sign == 100) %>%
  dplyr::group_by(cond) %>%
  dplyr::summarise(n = dplyr::n())
```

## [2.2.] Merged or individual peaksets
```{r}
peaks <- preSub %>%
  dplyr::filter(sign == 100) %>%
  dplyr::select(-sign) %>% 
  .GlobalEnv$merger(df = .)

peaks_nano <- preSub %>%
  dplyr::filter(
      cond == "cph_nanodam" &
      sign == 100
    )

peaks_tada <- preSub %>%
  dplyr::filter(
      cond == "cph_tada" &
      sign == 100
    )
```

## [2.3.] Center & edit peaks
#### conversion for 'peaks', 'peaks_tada', 'peaks_nano'
#### exchange 'peaks' with 'peaks_tada', 'peaks_nano'
```{r}
xmin = xmax = 2500L
peaks_gr <- GenomicRanges::GRanges(peaks)
wins_cen <- IRanges::resize(
    x = peaks_gr,
    width = 1,
    fix = "center"
  )
wins_reg <- GenomicRanges::promoters(
      x = wins_cen,
      upstream = xmin,
      downstream = xmax
    ) %>%
  IRanges::trim()
```

## [2.4.] Build sequence of genomic steps
```{r}
bin = 10L
steps <- base::seq(-xmin, xmax, by = base::as.numeric(bin))
```

##--------------##
##----Tracks----##
##--------------##

## [3.0.] Identify bigwig files
#### files: "Cph_NanoDam_1_vs_Dam_NanoDam_1.bw"; "Cph_TaDa_1_vs_Dam_TaDa_1.bw"; "Dam_TaDa_2_vs_Dam_TaDa_1.bw"
```{r}
tracks_ <- base::list.files(
      path = base::paste0(
          here::here("data/")
        ),
      full.names = TRUE
    ) %>%
  stringr::str_subset("-vs-") %>%
  stringr::str_subset("bw")
```

```{r}
tracknames <- purrr::map_chr(
    .x = tracks_,
    .f = function(t){
      base::paste0(
        stringr::str_replace(
            string = base::basename(t),
            pattern = "^(.*?)(_R1.*)?-vs-.*$",
            replacement = "\\1"
          ),
        "-vs-",
        stringr::str_replace(
            string = base::basename(t),
            pattern = "^.*-vs-(.*?)(_R1.*)?\\..*$",
            replacement = "\\1"
          )
      )
    }
  )
```

## [3.1.] Build intensity matrices
#### evaluate with 'matrices[[1]][995:1005,]'
```{r}
tracks <- purrr::map(
    .x = tracks_,
    .f = rtracklayer::BigWigFile
  )
matrices <- purrr::map(
    .x = tracks,
    .f = .GlobalEnv$extract_matrix,
    regions = wins_reg,
    size = base::length(steps)
  )
base::names(matrices) <- tracknames
utils::str(matrices)
```

## [3.2.] Calculate means & stderrs
```{r}
comb_plot <- plyr::ldply(
      .data = matrices
    ) %>%
  tidyr::pivot_longer(
      cols = -.id,
      names_to = "position",
      values_to = "intensity"
    ) %>%
  dplyr::mutate(
      position = base::as.integer(position)
    ) %>%
  dplyr::group_by(.id,position) %>%
  dplyr::summarise(
      mean = base::mean(intensity, na.rm = TRUE),
      std = stats::sd(x = intensity, na.rm = TRUE)/
        base::sqrt(base::sum(!base::is.na(intensity))),
      .groups = "drop_last"
    ) %>%
  dplyr::mutate(
      step = steps
    )

ids = comb_plot %>%
  dplyr::distinct(.id) %>%
  dplyr::pull(.id)

conds = purrr::map_chr(
    .x = ids,
    .f  = function(id){
      return(
        stringr::str_replace(
          string = id,
          pattern = "(.*?)_S.*",
          replacement = "\\1"
        )
      )
    }
  )
```

## [3.3.] Plot data
```{r}
ggplot2::ggplot(
      data = comb_plot,
      mapping = aes(
        x = step,
        colour = .id,
        fill = .id
      )
    ) +
  geom_line(
      mapping = aes(
        y = mean
      ),
      size = 0.3
    ) +
  geom_ribbon(
      mapping = aes(
          ymin = mean - std,
          ymax = mean + std
        ),
      alpha = 0.5,
      outline.type = "full",
      colour = NA
    ) +
  scale_y_continuous(
      limits = base::c(-0.1,0.65),
      breaks = base::seq(-0.1,0.6,0.1)
    ) +
  scale_colour_manual(
      limits = ids,
      breaks = ids,
      values = base::c(
          base::rep("darkgreen",4),
          base::rep("darkred",4),
          "darkblue","lightblue"
        )
    ) +
  scale_fill_manual(
      limits = ids,
      breaks = ids,
      values = base::c(
          base::rep("darkgreen",4),
          base::rep("darkred",4),
          "darkblue","lightblue"
        )
    ) +
  theme_bw() +
  # lemon::coord_capped_cart(
  #     bottom = "both",
  #     left = "both"
  #   ) +
  theme(
        aspect.ratio = 1,
        #panel.border=element_blank(),
        #axis.line = element_line(), 
        axis.ticks = element_line(colour='black'),
        legend.position = "none"
      )
```

## [3.4.] Save contingency table
```{r}
for(ext in c("pdf", "png")){
    ggplot2::ggsave(
      filename = base::paste0(
          here::here("results/"),
          base::format(base::Sys.time(), "%Y%m%d"),
          "_enrichment",
          "_GATCbedgraph",
          "_NanoDamVsTaDa",
          "_quantNorm",
          "_tadaPeaks",
          "_inclDamVsDamCtrls",
          "_noLegend",
          ".", ext
        ),
      plot = ggplot2::last_plot(),
      device = ext,
      dpi = 300,
      width = 5,
      height = 5
    )
  }
```

##------------------------------##
##----Precision_recall_curve----##
##------------------------------##

## [4.0.] Identify peak files
#### individual replicates for NanoDam & TaDa
#### files: "Cph_NanoDam_1_vs_Dam_NanoDam_2.broadPeak"; "Cph_TaDa_1_vs_Dam_TaDa_1.broadPeak"; "Dam_NanoDam_2_vs_Dam_NanoDam_1.broadPeak"
```{r}
fns_ <- base::list.files(
      path = here::here("data"),
      recursive = TRUE,
      full.names = TRUE
    ) %>%
  stringr::str_subset("broadPeak") %>%
  .GlobalEnv$str_ignore("DamOnly") %>%
  .GlobalEnv$str_ignore("merge")

ctrl_nano <- base::paste0(
    here::here("data/"),
    "Dam_NanoDam_2_vs_Dam_NanoDam_1.broadPeak"
  )
ctrl_tada <- base::paste0(
    here::here("data/"),
    "Dam_TaDa_2_vs_Dam_TaDa_1.broadPeak"
  )

fns <- base::c(fns_,ctrl_nano,ctrl_tada)
```

## [4.1.] Helper function reader()
```{r}
reader <- function(f){
    return(
      readr::read_delim(
        file = f,
        delim = "\t",
        skip = 0,
        col_names = base::c(
            "chr","start","end",
            "name","score","strand",
            "signalValue","pValue","qValue"
          ),
        col_types = base::c(
          chr = readr::col_character(),
          start = readr::col_integer(),
          end = readr::col_integer(),
          name = readr::col_character(),
          score = readr::col_integer(),
          strand = readr::col_character(),
          signalValue = readr::col_double(),
          pValue = readr::col_double(),
          qValue = readr::col_double()
        )
      )
    )
  }
```

#### bg: fns[[1]] / fg: fns[2:8] ('dCTIP_nanodam_S7_R1_001-vs-Dam_nanodam_S10_R1_001_peaks')
#### bg: fns[[5]] / fg: fns[base::c(1:4,6:8)] ('dCTIP_tada_S7_R1_001-vs-Dam_tada_S8_R1_001_peaks')
```{r}
bg_nr = 5 #1
fg_nrs = purrr::discard(
    .x = 1:base::length(fns),
    .p = ~ .x == bg_nr
  )

bg <- .GlobalEnv$reader(f = fns[[bg_nr]]) %>%
  #dplyr::filter(qValue >= (-1)*log10(0.05)) %>%
  dplyr::arrange(dplyr::desc(qValue)) %>% 
  dplyr::mutate(
      rank = dplyr::row_number()
    ) %>%
  dplyr::select(chr,start,end,rank) %>%
  GenomicRanges::GRanges()


fg <- purrr::map(
    .x = fns[fg_nrs],
    .f = function(f){
      return(
        .GlobalEnv$reader(f = f) %>%
        #dplyr::filter(qValue >= (-1)*log10(0.05)) %>%
        dplyr::arrange(dplyr::desc(qValue)) %>% 
        dplyr::mutate(
            rank = dplyr::row_number()
          ) %>%
        dplyr::select(chr,start,end,rank) %>%
        GenomicRanges::GRanges()
      )
    }
  )
base::names(fg) <- fg_nrs

overlap <- purrr::map(
    .x = fg,
    .f = function(f){
      return(
        GenomicRanges::findOverlaps(
          select = "all",
          query = f,
          subject = bg,
          maxgap = -1,
          ignore.strand = TRUE
        )
      )
    }
  )
base::names(overlap) <- fg_nrs
```

## [4.2.] Calculate precision, recall (sensitivity), reverse specificity
#### individual NanoDam replicates: '.x = 1:3' / 'n <- base::basename(fns[id+1])'
#### all individual files: '.x = 1:7' / 'n <- base::basename(fns[id+1])'
#### evaluate with 'prc_roc_plot_ %>% dplyr::group_by(name) %>% dplyr::slice_tail(n=10)'
```{r}
prc_roc_plot <- purrr::map_dfr(
  .x = fg_nrs,
  .f = function(id){
    n <- base::basename(fns[id]) %>%
      stringr::str_replace(
          string = .,
          pattern = "^(.*)_peaks.*",
          replacement = "\\1"
        )
    not_fg <- GenomicRanges::mcols(
        fg[[base::as.character(id)]][
            !(GenomicRanges::mcols(fg[[base::as.character(id)]])[,"rank"] %in%
            overlap[[base::as.character(id)]]@from)
          ]
      )[,"rank"]

    return(
        fg[[base::as.character(id)]] %>%
          tibble::as_tibble() %>%
          dplyr::mutate(
            pres = purrr::map_lgl(
                .x = rank,
                .f = function(l){
                  l %in% overlap[[base::as.character(id)]]@from
                }
              ),
            not_incl_fg = base::length(not_fg),
            pres_nr = base::cumsum(pres),
            nonpres_nr = base::cumsum(!pres),
            prec = (pres_nr/(pres_nr + nonpres_nr)),
            recall = pres_nr/base::length(bg),
            rev_spec = nonpres_nr/base::length(not_fg),
            name = n
          )
      )
    }
  )
```

## [4.3.] Evaluation
```{r}
prc_roc_plot %>%
  dplyr::group_by(name) %>%
  dplyr::slice_tail(n=10)

overlap[["2"]]@from %>% unique %>% length
overlap[["2"]]@to %>% unique %>% length
```

## [4.4.] aucROC & aucPRC
```{r eval=FALSE}
x = prc_roc_plot$rev_spec
y = prc_roc_plot$recall
from = base::min(x, na.rm = TRUE)
to = base::max(x, na.rm = TRUE)
space.interp = base::sort(
  base::unique(
    base::c(from, to, x[x > from & x < to])
    )
  )
values <- stats::approx(
    x = x,
    y = y,
    xout = space.interp
  )
aucROC <- 0.5 * base::sum(
    base::diff(values$x) * (
        values$y[-1] + values$y[-length(values$y)]
      )
  )

x = prc_roc_plot$recall
y = prc_roc_plot$prec
from = base::min(x, na.rm = TRUE)
to = base::max(x, na.rm = TRUE)
space.interp = base::sort(
  base::unique(
    base::c(from, to, x[x > from & x < to])
    )
  )
values <- stats::approx(
    x = x,
    y = y,
    xout = space.interp
  )
aucPRC <- 0.5 * base::sum(
    base::diff(values$x) * (
        values$y[-1] + values$y[-length(values$y)]
      )
  )
```

## [4.5.] Plot PRC
```{r}
plot_prrec <- ggplot2::ggplot(
    data = prc_roc_plot,
    mapping = aes(
      y = prec,
      x = recall,
      colour = name
    )
  ) +
  geom_line() +
    scale_y_continuous(
      name = "precision"
    ) +
  scale_x_continuous(
      limits = base::c(0,1),
      name = "recall"
    ) +
  theme_bw() +
  theme(
    aspect.ratio = 1L
  )
base::print(plot_prrec)
```

## [4.6.] Print plot
```{r}
for(ext in c("pdf", "png")){
    ggplot2::ggsave(
      filename = base::paste0(
          here::here("results/"),
          bbase::format(base::Sys.time(), "%Y%m%d"),
          "_precisionRecall",
          ".", ext
        ),
      plot = plot_prrec,
      device = ext,
      dpi = 300,
      width = 6,
      height = 6
    )
  }
```

## [4.7.] Plot ROC
```{r}
lim <- prc_roc_plot_ %>%
  dplyr::distinct(name) %>%
  dplyr::pull(name)

plot_roc <- ggplot2::ggplot(
      data = prc_roc_plot,
      mapping = aes(
        x = rev_spec,
        y = recall,
        colour = name
      )
    ) +
  geom_line() +
  scale_y_continuous(
      limits = base::c(0,1),
      name = "sensitivity"
    ) +
  scale_x_continuous(
      name = "1 - specificity"
    ) +
  scale_colour_manual(
      limits = lim,
      breaks = lim,
      values = base::c(
        base::rep("#303ca2",4), #3
        base::rep("#737373",3), #4
        "#8b0000","#006400"
      )
    ) +
  theme_bw() +
  theme(
    aspect.ratio = 1L,
    legend.position = "none"
  )
base::print(plot_roc)
```

## [4.8.] Print plot
#### refs: "dCTIPTadaS7DamTadaS8", "dCTIPNanoS7DamNanoS10",
```{r}
for(ext in c("pdf", "png")){
    ggplot2::ggsave(
      filename = base::paste0( 
          here::here("results/"),
          base::format(base::Sys.time(), "%Y%m%d"),
          "_precisionRecall",
          "_NanoVsAll",
          "_ref", "dCTIPTadaS7DamTadaS8", 
          ".", ext
        ),
      plot = plot_roc,
      device = ext,
      dpi = 300,
      width = 5,
      height = 5
    )
  }
```

##------------------##
##----Complexity----##
##------------------##

## [5.0.] Identify files
```{r}
fns <- base::list.files(
      path = here::here("data/"),
      recursive = TRUE,
      full.names = TRUE
    ) %>%
  stringr::str_subset("preseq")
```

## [5.1.] Read in data
```{r}
ps_ <- purrr::map_dfr(
    .x = fns,
    .f = function(f){
      n <- stringr::str_replace(
          string = base::basename(f),
          pattern = "^(.*).preseq.*",
          replacement = "\\1"
        )
      return(
        readr::read_delim(
            file = f,
            delim = "\t",
            skip = 1,
            col_names = base::c("total_reads","distinct_reads"),
            col_types = readr::cols(
              .default = readr::col_double()
            )
          ) %>%
        dplyr::mutate(
          name = n
        )
      )
    }
  )
```

## [5.2.] Prepare data for plotting
```{r}
ps <- ps_ %>%
  dplyr::mutate(
      cond_ = stringr::str_replace(
          string = name,
          pattern = "^.*?_(.*?)_.*",
          replacement = "\\1"
        ),
      merg = dplyr::case_when(
          stringr::str_detect(name,"merge") ~ "merge",
          TRUE ~ "replicate"
        ),
      cond = base::paste0(cond_,"_",merg)
    ) %>%
  dplyr::select(-`cond_`,-merg) %>%
  dplyr::filter(!stringr::str_detect(cond, "merge"))

lim <- ps %>%
  dplyr::distinct(name) %>%
  dplyr::pull(name)
```

## [5.3.] Plot data
```{r}
col_1 <- base::c(
    "darkorange","orange","orange",
    "darkgreen", "green", "green",
    "darkred", "red", "red",
    "darkblue", "blue", "blue"
  )
col_2 <- base::c(
    base::rep("#3CB85D",2),
    base::rep("darkgreen",2),
    base::rep("red",2),
    base::rep("darkred",2)
  )

ggplot2::ggplot(
      data = ps,
      mapping = aes(
        x = total_reads,
        y = distinct_reads,
        colour = name
      )
    ) +
  geom_line() +
  geom_abline(
      intercept = 0,
      slope = 1,
      linetype = "dashed",
      colour = "grey65"
    ) +
  theme_bw() +
  scale_colour_manual(
      limits = lim,
      breaks = lim,
      values = col_2
    ) +
  theme(
      aspect.ratio = 1,
      legend.position = "none"
    )
```

## [5.4.] Print plot
```{r}
for(ext in c("pdf", "png")){
    ggplot2::ggsave(
      filename = base::paste0(
          here::here("results/"),
          base::format(base::Sys.time(), "%Y%m%d"),
          "_complexity",
          "_AllBamWoMerge",
          ".", ext
        ),
      plot = ggplot2::last_plot(),
      device = ext,
      dpi = 300,
      width = 5,
      height = 5
    )
  }
```
